### 2022-06-14 paper/main.tex
starting paper

\documentclass[12pt,oneside, letterpaper]{book}
\usepackage[utf8]{inputenc}
\usepackage{indentfirst}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{ragged2e}
\usepackage{setspace}
\usepackage{tabu}
\usepackage{geometry}

% Set margins
\geometry
{a4paper,
	top=2.0in,
	bottom=1.0in,
	left=1.5in,
	right=1.0in,
	headsep=0.0in,
	footskip=0.5in
}

% For inserting images
\usepackage{graphicx}
\graphicspath{ {./Images/} }

% For the references
\usepackage[sorting=none]{biblatex}
%\addbibresource{References.bib}

% Setting page numbers
\pagestyle{plain}
\pagenumbering{roman}
\justifying

% For making the list of abbreviations
\usepackage{nomencl}
\makenomenclature
\renewcommand{\nomname}{List of Abbreviations}

\begin{document}
% makes the page numbers roman numerals, doesn't count
% these pages in the table of contents

%Begin the title page
\begin{titlepage}
 \begin{center}

THESIS OR DISSERTATION TITLE IS CENTERED AND IN ALL CAPS.\\
THE FIRST LINE OF THE TITLE SHOULD BE TWO INCHES FROM.\\
THE TOP OF THE PAGE. SINGLE-SPACED.

 \vspace{6.5cm}

BY

\vspace{0.7cm}

AUTHOR NAME IN ALL CAPITAL LETTERS

\vspace{0.7cm}

B\textit{X}, College of University, YYYY\\
M\textit{X}, College of University, YYYY

\vfill 
\vspace{0.8cm}

SPECIFY DISSERTATION OR THESIS

\vspace{0.8cm}

Submitted in partial fulfillment of the requirements for\\
the degree of Name of Degree in Major\\
in the Graduate School of\\
Binghamton University\\
State University of New York\\
YYYY

   \end{center}
\end{titlepage}

%Begin the copyright page
\newpage

\thispagestyle{empty}

\vbox to 8.0truein{}

\centerline{\copyright\ Copyright by Full Legal Name of Author YYYY}

\

\centerline{All Rights Reserved}

%Begin the committee member page
\newpage
\addtocounter{page}{1}

{\baselineskip = 10pt

\vbox to 5.5truein{}

\centerline{Accepted in partial fulfillment of the requirements for}
\centerline{the degree of Name of Degree in Major}
\centerline{in the Graduate School of}
\centerline{Binghamton University}
\centerline{State University of New York}
\centerline{YYYY}

\

\centerline{Month DD, YYYY}

\

\centerline{First Name Last Name, Chair}
\centerline{Department of XXXXXX, University Name}
\

\centerline{First Name Last Name, Faculty Advisor}
\centerline{Department of XXXXXX, University Name}
\

\centerline{First Name Last Name, Member}
\centerline{Department of XXXXXX, University Name}
\

\centerline{First Name Last Name, Outside Examiner}
\centerline{Department of XXXXXX, University Name}
}

\newpage
\newgeometry
{a4paper,
	top=1.0in,
	bottom=1.0in,
	left=1.5in,
	right=1.0in,
	headsep=0.0in,
	footskip=0.5in
}
\newcommand{\chapfnt}{\fontsize{18}{18}}
\newcommand{\secfnt}{\fontsize{14}{14}}
\newcommand{\ssecfnt}{\fontsize{12}{12}}
\setstretch{2.0}

\titleformat{\chapter}[hang]
{\normalfont\chapfnt\bfseries\centering}{\thechapter\ }{1em}{}
\titlespacing*{\chapter}{0pt}{1in}{12pt}

\titleformat{\section}
{\normalfont\secfnt\bfseries}{\thesection}{1em}{}

\titleformat{\subsection}
{\normalfont\ssecfnt\bfseries}{\thesubsection}{1em}{}

\chapter*{Abstract}
\par The abstract is mandatory.
\par The maximum acceptable length for an abstract to be published in Dissertation Abstracts International (DAI) is 350 words. The maximum acceptable length for an abstract to be published in Master’s Thesis Directories (MTD) is 150 words. However, an abstract within the dissertation or thesis need not be limited. The student may prepare a lengthy abstract for inclusion in the thesis or dissertation and a more concise summary for publication in DAI/MTD. 
\par The abstract is expected to give a succinct account of the student's work so that a reader can quickly learn the essential contents and results. A typical abstract includes a statement of the problem, an account of procedure or methods followed, and an account of main results and conclusions.
\par Abstracts must be prepared carefully, since they are published in DAI/MTD without editing or revision.

\newpage

\vbox to 4.25truein{}
\centerline{The dedication is optional. Type your dedication here, centered on the page.}

\newpage
\begin{doublespace}
\chapter*{Acknowledgements}
\par The Acknowledgements section is optional. Here, type your acknowledgements. Double-space. If your style guide of choice (e.g., MLA, APA, Chicago, etc.) gives specific formatting guidelines, follow them.
\end{doublespace}

\newpage
\begin{doublespace}
\chapter*{Preface}
\par The preface is optional. If necessary, the following information should be included:
\par For previously published works, cite each published piece fully and indicate whether your studies or articles are being republished in their entirety and in the original wording, or whether they have been revised for the dissertation. Indicate that your studies or articles are being included because they were part of the programmatic line of research that comprised the dissertation and that including them provides a coherent and appropriately sequenced investigation. Describe your (the dissertation author) role in the published work. Certify that permission to republish these works in the dissertation has been obtained from the publisher or owner. 
\par For images, identify the ones for which permission has been received by figure number and with reference to the copyright holder (whether an individual or institution) and certify that permission has been obtained. You may wish to add that all other images are in the public domain or being used under a public license or fair use. 
\end{doublespace}
\newpage

\setstretch{1.0}
\tableofcontents
\listoftables
\addcontentsline{toc}{chapter}{List of Tables}

\listoffigures
\addcontentsline{toc}{chapter}{List of Figures}

\addcontentsline{toc}{chapter}{List of Abbreviations}
\chapter*{List of Abbreviations}
Include any listing of abbreviations on this page.
%\printnomenclature

\mainmatter
\setstretch{2.0}

\chapter{Introduction}
\par The following text is only included to take up space and provide a visual sense of the layout of your paper.   It is written in Latin for no reason other than to encourage you to bypass it as not being necessary information for you to spend your time reading.  
\par Sed ut perspiciatis unde omnis iste natus error sit voluptatem accusantium doloremque laudantium, totam rem aperiam, eaque ipsa quae ab illo inventore veritatis et quasi architecto beatae vitae dicta sunt explicabo. Nemo enim ipsam voluptatem quia voluptas sit aspernatur aut odit aut fugit, sed quia consequuntur magni dolores eos qui ratione voluptatem sequi nesciunt. Neque porro quisquam est, qui dolorem ipsum quia dolor sit amet, consectetur, adipisci velit, sed quia non numquam eius modi tempora incidunt ut labore et dolore magnam aliquam quaerat voluptatem. Ut enim ad minima veniam, quis nostrum exercitationem ullam corporis suscipit laboriosam, nisi ut aliquid ex ea commodi consequatur? Quis autem vel eum iure reprehenderit qui in ea voluptate velit esse quam nihil molestiae consequatur, vel illum qui dolorem eum fugiat quo voluptas nulla pariatur?

\chapter{Background and Related Work}
\par Each chapter should begin at the top of a new page, with a two-inch top margin.\footnote{This is your first footnote, if your chosen style manual calls for footnotes rather than endnotes. \\} 
\par Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.\footnote{This is your second footnote. There should be a space, as shown, between each note (whether footnote or endnote).}

\section{Media, Politics, and Perception of Crime}
\par TODO: papers about historical media and crime, modern issues, social media effects

\section{Geography}
\par TODO: explanation of geographical terms (urban areas, MSAs, etc)

\section{Reddit as Social Media}
\par TODO: what reddit is and its role in misinformation

\begin{figure}[ht]
    \centering
    \begin{minipage}[t]{0.8\textwidth}
    \textit{Follow this list to ensure your pages are in the correct order. \\}
	\begin{enumerate}
	    \item Title page (mandatory)
	    \item Copyright notice (mandatory)
	    \item Committee page (mandatory)
	    \item Abstract (mandatory)
	    \item Dedication (optional)
	    \item Acknowledgments (optional)
	    \item Preface (optional)
	    \item Table of contents (mandatory)
	    \item List of tables (include list if manuscript includes tables)
	    \item List of figures (include list if manuscript includes figures)
	    \item List of plates (include list if manuscript includes plates)
	    \item List of abbreviations (include if needed)
	    \item Body of manuscript (mandatory)
	    \item Appendix(es) (if necessary)
	    \item Notes (include if necessary)
	    \item Bibliography (mandatory)
	\end{enumerate}
	\end{minipage}
    \caption{Sequence of pages for thesis or dissertation.}
	\label{fig:fig-1}
\end{figure}

\begin{table}[h!]
    \small
    \caption{General formatting requirements for thesis or dissertation}
    %\begin{tabu} to 1.0\textwidth {| *{3}{c|} }
    \begin{tabular}{| m{1.25in} | m{3in} | m{0.75in} |}
    \hline
    \multicolumn{2}{|c|}{Formatting Requirement} & Fulfilled? \\ \hline
    Page margins & \begin{tabular}{ll}
        \begin{tabular}{c|c}
        Left & 1.5" \\ \hline
        Right & 1" \\ \hline
        Top & 1" \\ \hline
        Bottom & 1" \\ 
        \end{tabular} 
         &
        \begin{tabular}{c}
             {\scriptsize The 1.5” left margin } \\ 
             {\scriptsize leaves room for the } \\
             {\scriptsize manuscript to be bound.} 
        \end{tabular}
    \end{tabular} & \ \\ \hline
    Body text of manuscript & Double-spaced. Justifying the text at the right margin is optional & \  \\ \hline
    Font size & No smaller than 10-point and no larger than 14-point & \  \\ \hline
    Text color & All text should be black (including URLs) & \  \\ \hline
    New chapter & Each chapter begins at the top of a new page, with a 2” top margin & \  \\ \hline
    Prefatory headings, chapter names and section headings & All prefatory headings, chapter names and section headings should be formatted consistently & \  \\ \hline
    Footnotes or endnotes & Single-spaced, with a double space between each note & \  \\ \hline
    Bibliographic entries / works cited / references & Single-spaced, with an extra space between entries. Style and format should otherwise follow the style guide used for the rest of the thesis/dissertation & \  \\ \hline
    Long quotations & May be indented and single-spaced, though some style guides prefer them to be indented and double-spaced & \  \\ \hline
    Tables and figures & Must conform to the same margins as the text. If the table or figure is placed in landscape orientation (horizontally on page), the margins and page-number location must retain a portrait (vertical) orientation, as on a regular page. Tables and figures may be in color & \  \\ \hline
    Table and figure captions & Single-spaced. Should be in the same type as the body of the text & \  \\ \hline
    Hand lettering & Not permitted. Symbols, accent marks, and equations must be typescript & \  \\ \hline
    Corrections in pen or pencil & Not permitted. & \  \\ \hline
    Printed manuscript & Single-sided (simplex). Do not staple. Do not hole-punch. The manuscript should be clearly readable throughout, for both electronic and printed documents. Any photocopies should be checked to make sure they are legible. If there are questions regarding print quality, you are encouraged to consult The Graduate School & \  \\ \hline
	\end{tabular}
	\label{table:table-1}
\end{table}

\chapter{Subreddit-level Analysis}

\section{Data Overview}
\par The subreddit-level analysis requires a variety of different data inputs. These data inputs can be divided into two major subcategories: post and comment data from Reddit itself and data that provide contextual or qualitative information.

\subsection{Reddit Data}
\par The Reddit dataset contains posts from the subreddits of the 384 MSAs of the United States as of March 2020 (REF). Appendix (REF) provides a full list of subreddits used. From this list of subreddits, we scrape and store all posts that users submit. In total, 161,166 posts were gathered between April 5, 2022 and May 31, 2022. (REF - Figure of timeline). The datastore archives posts in two formats. First, posts are written to a system of record to ensure that there is an authoritative data source that can be referenced. Second, pertinent information, such as post title and author, is extracted from the posts data stream and placed in a separate datastore.

\par After storing data, an analysis tool runs to determine if a post is about crime. To do this, a regular expression checks if a post's title or a post's link's URL contains a crime-related keyword. Appendix (REF) lists the keywords used. These keywords were derived from actions that constitute violent crime and their synonyms, as well as generic crime-related words. If the regular expression returns a hit, a flag is raised in the database denoting that the post is about crime. Overall, 6,792 posts are estimated to discuss crime.

\subsection{Contextual Data}
\par A variety of data were utilized to highlight trends in the Reddit posts. One variable that subreddits are compared to is population size of the MSA (REF). These values range from a minimum of 58,639 (Carson City, NV) and a maximum of 20,140,470 (New York-Newark-Jersey City, NY-NJ-PA). MSAs are categorized into four bins based on their size: large, medium, small, and very small. The population cutoffs are 1,000,000, 500,000, and 200,000. The large population contains 56 members, the medium bin contains 54 members, the small bin contains 113 members, and the very small bin contains 161 members. Appendix (REF) contains the populations of all MSAs.

\par Another variable that provides context is the political climate of an MSA. For this, we consider the results of the 2020 election (REF) in terms of the percent of the MSA voting Democrat. These values range from a minimum of 20.2\% (Morristown, TN) to a maximum of 80.9\% (Santa Cruz-Watsonville, CA). The MSAs are categorized into five bins based on their voting results: Very Conservative, Conservative, Moderate, Liberal, and Very Liberal. The percentage cutoffs for the bins are 37.5\%, 47.5\%, 52.5\%, and 62.5\%. The Very Conservative bin contains 112 members, the Conservative bin contains 103 members, the Moderate bin contains 57 members, the Liberal bin contains 73 members, and the Very Liberal bin contains 39 members. Appendix (REF) contains the voting patterns of all MSAs.

\par A third variable that is considered is the documented violent crime rate of each MSA. This data is derived from the FBI's Uniform Crime Reporting statistics (REF / Footnote) \footnote{Data from the FBI mostly comes from the year that is most recent, 2019. However, not all municipalities report information, so there are slight estimations in the data (REF). Additionally, not all MSAs have documented 2019 data, so 2018 or 2017 data are used instead. The year gathered is documented in Appendix (REF)}. These values range from a minimum of 44.3/100,000 (Bangor, ME) to a maximum of 1,397.2/100,000 (Birmingham-Hoover, AL). Documented crime data is also normalized using min-max normalization so that it can be compared to a similarly normalized crime discussion value from the Reddit data. Appendix (REF) contains the documented crime rate of all MSAs.

\section{Methods}
\par TODO: talk about code design.

\section{Results}
\par TODO: show graphs, maps, tables, etc. Discuss results in subsections

\begin{figure}[ht]
    \includegraphics[width=\textwidth]{Images/BingAerial.jpg}
    \caption{Aerial photograph of the Clock Tower, Peace Quad, and the Glenn G. Bartle Library Tower, June 16, 2009. This photograph was taken with a camera attached to a remote-controlled helicopter.}
    \label{fig:fig-2}
\end{figure}

\chapter{User-level Analysis}
\par TODO

\section{Data Overview}
\par TODO: talk about sample of users and their data

\section{Methods}
\par TODO: talk about code design

\section{Results}
\par TODO: discuss results

\chapter{Conclusion}

\newpage
\chapter*{Appendix A}
\addcontentsline{toc}{chapter}{Appendix A}

\newpage
\chapter*{Notes}
\addcontentsline{toc}{chapter}{Notes}

\newpage
\addcontentsline{toc}{chapter}{Bibliography/ References/ Works Cited}
\chapter*{Bibliography/ References/ Works Cited}
\setstretch{1.0}
\fontsize{10}{10pt} \selectfont
References should be single-spaced. The style and format for references should follow the style guide used for the rest of the dissertation. \newline \newline
Put an extra space in between entries.

% Remove lines 284, 287-288 and uncomment lines 291-292 while using template
%\renewcommand{\bibname}{Bibliography/References/Works Cited}
%\printbibliography

\end{document}

### 2022-06-15 paper/main.tex
adding methods

@@
 \section{Methods}
-\par TODO: talk about code design.
+\par We use one main scraper to gather post data from Reddit.
+This scraper utilizes multiple different tools to gather disparate pieces of data and place them into two datastores.
+This scraper prioritizes resilience to ensure that all posts are accounted for.
+Additionally, the scraper checks for new posts once every hour so that posts can be fetched before a user deletes them or a moderator deletes them.
+These communities are generally slow moving, with an average of 111 posts an hour between all 384 subreddits.
+
+\par To gather the data, the scraper first sends requests to the Reddit REST API (REF).
+We use the \texttt{new} endpoint for each subreddit to check the most recent posts.
+The post last written to the database for each subreddit is cached in a database table so that we can take advantage of the \texttt{after} parameter of the API.
+This parameter allows us to take posts that have been created since a given post ID.
+This parameter is especially useful on slower subreddits; without it, we would be performing requests on posts that might be months old.
+If the cached value does not exist or is not valid, then the most recent hundred posts are gathered.
+This is the maximum allowable value by the Reddit API.
+
+\par After performing error checking to ensure all of our requests went through, each record is sent to two databases.
+The first is a CockroachDB database that acts as a system of record.
+Raw posts are stored here in a simple format: \texttt{id}, \texttt{timestamp}, and \texttt{data}, which is the data retrieved from the Reddit API in JSON format.
+After writing to CockroachDB, the scraper then writes the JSON data from Reddit to ElasticSearch.
+ElasticSearch provides quick and efficient text analysis that allows for the extraction of certain keywords in post titles and URLs.
+
+\par The scraper and databases run in Docker containers.
+Containerization allows the tool, as well as the databases, to run in a clean, isolated environment without worrying about being choked out by other processes.
+Additionally, the tool-container is scheduled by Kubernetes to allow for a higher degree of availability and resilience.
+If something unexpected occurs and the tool goes down, it will simply be restarted by Kubernetes.
+Figure (REF) details the entire data scraping process.
 

### 2022-06-16 paper/main.tex
added to analysis

@@
 
-\begin{table}[h!]
-    \small
-    \caption{General formatting requirements for thesis or dissertation}
-    %\begin{tabu} to 1.0\textwidth {| *{3}{c|} }
-    \begin{tabular}{| m{1.25in} | m{3in} | m{0.75in} |}
-    \hline
-    \multicolumn{2}{|c|}{Formatting Requirement} & Fulfilled? \\ \hline
-    Page margins & \begin{tabular}{ll}
-        \begin{tabular}{c|c}
-        Left & 1.5" \\ \hline
-        Right & 1" \\ \hline
-        Top & 1" \\ \hline
-        Bottom & 1" \\ 
-        \end{tabular} 
-         &
-        \begin{tabular}{c}
-             {\scriptsize The 1.5” left margin } \\ 
-             {\scriptsize leaves room for the } \\
-             {\scriptsize manuscript to be bound.} 
-        \end{tabular}
-    \end{tabular} & \ \\ \hline
-    Body text of manuscript & Double-spaced. Justifying the text at the right margin is optional & \  \\ \hline
-    Font size & No smaller than 10-point and no larger than 14-point & \  \\ \hline
-    Text color & All text should be black (including URLs) & \  \\ \hline
-    New chapter & Each chapter begins at the top of a new page, with a 2” top margin & \  \\ \hline
-    Prefatory headings, chapter names and section headings & All prefatory headings, chapter names and section headings should be formatted consistently & \  \\ \hline
-    Footnotes or endnotes & Single-spaced, with a double space between each note & \  \\ \hline
-    Bibliographic entries / works cited / references & Single-spaced, with an extra space between entries.
-Style and format should otherwise follow the style guide used for the rest of the thesis/dissertation & \  \\ \hline
-    Long quotations & May be indented and single-spaced, though some style guides prefer them to be indented and double-spaced & \  \\ \hline
-    Tables and figures & Must conform to the same margins as the text.
-If the table or figure is placed in landscape orientation (horizontally on page), the margins and page-number location must retain a portrait (vertical) orientation, as on a regular page.
-Tables and figures may be in color & \  \\ \hline
-    Table and figure captions & Single-spaced. Should be in the same type as the body of the text & \  \\ \hline
-    Hand lettering & Not permitted. Symbols, accent marks, and equations must be typescript & \  \\ \hline
-    Corrections in pen or pencil & Not permitted. & \  \\ \hline
-    Printed manuscript & Single-sided (simplex).
-Do not staple.
-Do not hole-punch.
-The manuscript should be clearly readable throughout, for both electronic and printed documents.
-Any photocopies should be checked to make sure they are legible.
-If there are questions regarding print quality, you are encouraged to consult The Graduate School & \  \\ \hline
-	\end{tabular}
-	\label{table:table-1}
-\end{table}
-
 \chapter{Subreddit-level Analysis}
@@
 Second, pertinent information, such as post title and author, is extracted from the posts data stream and placed in a separate datastore.
+
+(FIG)
 
@@
 \par A third variable that is considered is the documented violent crime rate of each MSA.
-This data is derived from the FBI's Uniform Crime Reporting statistics (REF / Footnote) \footnote{Data from the FBI mostly comes from the year that is most recent, 2019.
+This data is derived from the FBI's Uniform Crime Reporting statistics (REF) \footnote{Data from the FBI mostly comes from the year that is most recent, 2019.
 However, not all municipalities report information, so there are slight estimations in the data (REF).
@@
 
+(FIG)
+
 \section{Results}
-\par TODO: show graphs, maps, tables, etc. Discuss results in subsections
+
+\subsection{Activity}
+
+\par In total, the Reddit scraper gathered 161,166 posts between 384 subreddits.
+Posts were collected between April 5th, 2022 to May 31, 2022.
+Table \ref{table:table-1} details the ten most active subreddits of those monitored.
+Similarly, Table \ref{table:table-2} lists the ten most active subreddits when normalized by population.
+
+\begin{table}[h!]
+    \centering
+    \small
+    \caption{Most active Metropolitan Areas}
+    %\begin{tabu} to 1.0\textwidth {| *{3}{c|} }
+    \begin{tabular}{| c | c | c |}
+    \hline
+    Metropolitan Statistical Area & Number of Posts & Population\\ \hline
+    Austin-Round Rock-Georgetown, TX & 4,084 & 2,283,371 \\ \hline
+    San Diego-Chula Vista-Carlsbad, CA & 3,265 & 3,298,634 \\ \hline
+    Boston-Cambridge-Newton, MA-NH & 3,120 & 4,941,632 \\ \hline
+    Denver-Aurora-Lakewood, CO & 2,785 & 2,963,821 \\ \hline
+    Chicago-Naperville-Elgin, IL-IN-WI & 2,673 & 9,618,502 \\ \hline
+    Sacramento-Roseville-Folsom, CA & 2,668 & 2,397,382 \\ \hline
+    Philadelphia-Camden-Wilmington, PA-NJ-DE-MD & 2,541 & 6,245,051 \\ \hline
+    Columbus, OH & 2,533 & 2,138,926 \\ \hline
+    Portland-Vancouver-Hillsboro, OR-WA & 2,526 & 2,512,859 \\ \hline
+    San Francisco-Oakland-Berkeley, CA & 2,476 & 4,749,008 \\ \hline
+	\end{tabular}
+	\label{table:table-1}
+\end{table}
+
+\par The most active MSAs by total number of posts share some common, predictable traits.
+First, all of the Metropolitan Areas listed have populations above 1,000,000.
+While expected, some notable MSAs were not included, such as New York-Newark-Jersey City, NJ-NJ-PA and Los Angeles-Long Beach-Anaheim, CA, which have populations of 20,140,470 and 13,200,998, respectfully.
+One possible explanation for these discrepancies is the fact that there is no uniform, consistent moderation policy among subreddits (REF).
+For example, some subreddits automatically filter out all posts and manually approve them, or they disallow certain types of posts (REF - nyc n chicago rules).
+
+\begin{table}[h!]
+    \centering
+    \small
+    \caption{Most active Metropolitan Areas per population}
+    %\begin{tabu} to 1.0\textwidth {| *{3}{c|} }
+    \begin{tabular}{| c | c | c |}
+    \hline
+    Metropolitan Statistical Area & Number of Posts & Population\\ \hline
+    Bellingham, WA & 1,381 & 226,847 \\ \hline
+    Bloomington, IN & 799 & 161,039 \\ \hline
+    Missoula, MT & 449 & 117,922 \\ \hline
+    Bend, OR & 660 & 198,253 \\ \hline
+    Burlington-South Burlington, VT & 546 & 171,415 \\ \hline
+    Corvallis, OR & 298 & 95,184 \\ \hline
+    Eugene-Springfield, OR & 1,183 & 382,971 \\ \hline
+    Charlottesville, VA & 638 & 221,524 \\ \hline
+    Ithaca, NY & 299 & 105,740 \\ \hline
+    Asheville, NC & 1,312 & 469,015 \\ \hline
+	\end{tabular}
+	\label{table:table-2}
+\end{table}
+
+\par The list of most active MSAs when accounting for population also have some common traits.
+These MSAs are generally politically liberal (REF) and have large college age populations (REF).
+These areas have large populations of people that fall under Reddit's main demographic (REF) and, as a result, have correspondingly active communities.
+
+\subsection{Crime Discussion}
+
+\par To first understand the relationship between certain socio-economic variables and the rate of crime discussion, we must first look at crime discussion percentages independently.
+Of the 161,166 posts gathered, 6,792 are determined to discuss crime by matching certain crime-related keywords to post titles and URLs.
+Table \ref{table:table-3} lists the Metropolitan Areas with the largest percentage of crime discussion from the total number of posts.
+
+\begin{table}[h!]
+    \centering
+    \small
+    \caption{Metropolitan Areas with most crime discussion}
+    %\begin{tabu} to 1.0\textwidth {| *{3}{c|} }
+    \begin{tabular}{| c | c | c |}
+    \hline
+    Metropolitan Statistical Area & \% Crime Posts & \# Crime Posts \\ \hline
+    Seattle-Tacoma-Bellevue, WA & 18.2 & 344 \\ \hline
+    Anniston-Oxford, AL & 15.7 & 8 \\ \hline
+    Lewiston-Auburn, ME & 15.4 & 14 \\ \hline
+    Bay City, MI & 14.0 & 7 \\ \hline
+    Lewiston, ID-WA & 13.0 & 7 \\ \hline
+    Pine Bluff, AR & 12.5 & 4 \\ \hline
+    Los Angeles-Long Beach-Anaheim, CA & 12.0 & 257 \\ \hline
+    Portland-Vancouver-Hillsboro, OR-WA & 11.4 & 287 \\ \hline
+    Rocky Mount, NC & 11.3 & 7 \\ \hline
+    Decatur, AL & 10.9 & 7 \\ \hline
+    New York-Newark-Jersey City, NY-NJ-PA & 10.7 & 196 \\ \hline
+    Flint, MI & 9.7 & 10 \\ \hline
+    Morristown, TN & 9.3 & 4 \\ \hline
+    Sumter, SC & 9.3 & 5 \\ \hline
+    Vallejo, CA & 8.8 & 9 \\ \hline
+	\end{tabular}
+	\label{table:table-3}
+\end{table}
+
+\par On a greater scale, Figure (REF) displays the cumulative distribution function of the data. The average crime discussion percentage lays at 3.5\%.
+
+(FIG)
+
+\par Furthermore, Figure (REF) displays a map of all Metropolitan Areas by the percentage of crime posts submitted to their respective subreddits.
+The darker the shade of green, the more posts discuss crime.
+
+(FIG)
+
+\subsection{Crime Discussion and Population}
+
+\subsection{Crime Discussion and Politics}
+
+\subsection{Crime Discussion and Documented Crime}
 
@@
 
+% Appendix A - Metro, subreddit, population, hits
+% Appendix B - Metro, population, pop class, Pcrime rate
+% Appendix C - Metro, percent dem, pol class, pcrime rate
+% Appendix D - Metro, normalized cr, normalized pcr
+% Appendix E - Keywords
+
 \newpage

### 2022-06-17 paper/main.tex
added more to analysis

@@
 
-\par On a greater scale, Figure (REF) displays the cumulative distribution function of the data. The average crime discussion percentage lays at 3.5\%.
-
-(FIG)
-
 \par Furthermore, Figure (REF) displays a map of all Metropolitan Areas by the percentage of crime posts submitted to their respective subreddits.
 The darker the shade of green, the more posts discuss crime.
+The average crime discussion percentage lays at 3.5\%.
 
@@
 
+\par The 384 MSAs of the United States vary greatly in terms of their actual population sizes.
+Once the Urban Area that makes the core of the Statistical Area reaches a population of at least 50,000, a Metropolitan Area forms in the county (or counties) that the Urban Area lies in.
+As a result of this definition, we break down MSAs into the four categories based on size discussed previously: very small, small, medium, and large.
+We use these categorizations to help explain trends in data relating to MSA population sizes.
+
+\par To identify any potential trends in the population data, we take the mean crime discussion value of each bucket category.
+Figure (REF) displays the average min-max normalization score for the percentage of crime discussion based on population size.
+Here, the very small population bucket contains 161 members with an average normalized score of 0.196, the small bucket contains 113 members with an average score of 0.173, the medium bucket contains 54 members with an average score of 0.166, and the large bucket contains 56 members with an average score of 0.260.
+
+(FIG)
+
+\par Figure (REF) provides average normalized scores for documented crime to compare trends to crime discussion.
+We can see that as population increases, documented crime rates gradually increase.
+This trend is semi-reflected in the crime discussion data.
+Crime discussion scores are roughly equivalent for the very small, small, and medium buckets.
+However, the large population bucket has a significantly higher crime discussion score than the other buckets.
+The large population bucket has a 6\% greater score than the medium population bucket when comparing documented crime data, but the large population bucket has a 56\% greater score than the medium population bucket when comparing crime discussion data.
+
+\par Figure (REF) shows a cumulative distribution function of the data by population bucket.
+Here, we can see that the mean large population MSA has a fairly tight distribution, while the mean very small population MSA has a more spread out distribution.
+
+(FIG)
+
 \subsection{Crime Discussion and Politics}
 
-\subsection{Crime Discussion and Documented Crime}
+\par Similarly to population data, political affiliation is one possible variable that can sway crime discussion.
+To measure this, we look at the results of the 2020 presidential election.
+We consider the number of votes that the Democratic and Republic parties received as stand-ins for liberal and conservative political views, respectfully.
+Political affiliation of the 384 MSAs is broken down into the five categories discussed earlier: very conservative, conservative, moderate, liberal, and very liberal.
+Figure (REF) shows a map of the political affiliation of all Metropolitan Areas in the United States.
+
+(FIG)
+
+\par In identifying trends based on politics, we follow a familiar method and take the mean crime discussion value of each political class.
+Figure (REF) displays the average min-max normalization score for crime discussion and reported crime for each political class.
+Here, the very conservative bucket contains 112 members with a mean score of 0.170, the conservative bucket contains 103 members with a mean score of 0.179, the moderate bucket contains 57 members with a mean score of 0.207, the liberal bucket contains 73 members with a mean score of 0.201, and the very liberal bucket contains 39 members with a mean score of 0.274.
+
+(FIG)
+
+\par When looking at crime discussion rates, we can see that more liberal cities have the highest rates of crime discussion.
+The very liberal class has a 32\% higher crime discussion score than the next largest value.
+The two conservative political classes have the lowest crime discussion scores.
+However, these trends are not reflected in the documented crime rate scores.
+Figure (REF) shows that very liberal MSAs have a lower mean documented crime rate than more conservative areas.
+Very liberal areas are also the only class in which the crime discussion score is higher than the reported crime rate score.
+
+(FIG)
+
+\par Figure (REF) shows two scatterplots: one which shows the percent crime discussion in relation to politics among medium and large sized MSAs and the other which shows the documented crime rate among the same sample group in relation to politics.
+The shades of the dots represent their political class.
+From the trendline in the data, we can see that as areas become more liberal, their crime discussion percentages increase fairly rapidly.
+The most conservative member of the plot, Provo-Orem, UT, did not include a single post discussing crime, while more liberal areas such as Seattle, Los Angeles, Portland, and New York City had values over 10\%.
+In contrast, when looking at the documented violent crime rate among large and mid-size MSAs, more liberal areas generally have lower average crime rates.
+MSAs that lean conservative, such as Birmingham-Hoover, AL and Kansas City, MO-KS have among the highest crime rates, as well as more politically moderate cities, such as Memphis, TN-MS-AR.
+
+\subsection{Crime Discussion and Reported Crime}
 

### 2022-06-17 paper/main.tex
added some figures

@@
 
-\par Furthermore, Figure (REF) displays a map of all Metropolitan Areas by the percentage of crime posts submitted to their respective subreddits.
+\par Furthermore, Figure \ref{fig:map-1} displays a map of all Metropolitan Areas by the percentage of crime posts submitted to their respective subreddits.
 The darker the shade of green, the more posts discuss crime.
@@
 
-(FIG)
+\begin{figure}[ht]
+    \includegraphics[width=\textwidth]{Images/PCrime.png}
+    \caption{Map of crime discussion by MSA}
+    \label{fig:map-1}
+\end{figure}
 
@@
 \par To identify any potential trends in the population data, we take the mean crime discussion value of each bucket category.
-Figure (REF) displays the average min-max normalization score for the percentage of crime discussion based on population size.
+Figure \ref{fig:graph-1} displays the average min-max normalization score for the percentage of crime discussion based on population size.
 Here, the very small population bucket contains 161 members with an average normalized score of 0.196, the small bucket contains 113 members with an average score of 0.173, the medium bucket contains 54 members with an average score of 0.166, and the large bucket contains 56 members with an average score of 0.260.
 
-(FIG)
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.75\textwidth]{Images/bar-population.png}
+    \caption{Comparison of discussed crime and documented crime by population}
+    \label{fig:graph-1}
+\end{figure}
 
-\par Figure (REF) provides average normalized scores for documented crime to compare trends to crime discussion.
+\par Figure \ref{fig:graph-1} provides average normalized scores for documented crime to compare trends to crime discussion.
 We can see that as population increases, documented crime rates gradually increase.
@@
 Political affiliation of the 384 MSAs is broken down into the five categories discussed earlier: very conservative, conservative, moderate, liberal, and very liberal.
-Figure (REF) shows a map of the political affiliation of all Metropolitan Areas in the United States.
+Figure \ref{fig:map-2} shows a map of the political affiliation of all Metropolitan Areas in the United States.
 
-(FIG)
+\begin{figure}[ht]
+    \includegraphics[width=\textwidth]{Images/pol.png}
+    \caption{Map of 2020 Presidential Election Results by MSA}
+    \label{fig:map-2}
+\end{figure}
 
 \par In identifying trends based on politics, we follow a familiar method and take the mean crime discussion value of each political class.
-Figure (REF) displays the average min-max normalization score for crime discussion and reported crime for each political class.
+Figure \ref{fig:graph-2} displays the average min-max normalization score for crime discussion and reported crime for each political class.
 Here, the very conservative bucket contains 112 members with a mean score of 0.170, the conservative bucket contains 103 members with a mean score of 0.179, the moderate bucket contains 57 members with a mean score of 0.207, the liberal bucket contains 73 members with a mean score of 0.201, and the very liberal bucket contains 39 members with a mean score of 0.274.
 
-(FIG)
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.75\textwidth]{Images/bar-politics.png}
+    \caption{Comparison of discussed crime and documented crime by politics}
+    \label{fig:graph-2}
+\end{figure}
 
@@
 However, these trends are not reflected in the documented crime rate scores.
-Figure (REF) shows that very liberal MSAs have a lower mean documented crime rate than more conservative areas.
+Figure \ref{fig:graph-2} shows that very liberal MSAs have a lower mean documented crime rate than more conservative areas.
 Very liberal areas are also the only class in which the crime discussion score is higher than the reported crime rate score.
 
-(FIG)
+\begin{figure}[!tbp]
+  \centering
+  \begin{minipage}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{Images/scatter-politics-mid-large.png}
+    \caption{Perceived crime by political leaning}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{Images/scatter-crime-mid-large.png}
+    \caption{Documented crime by political leaning}
+  \end{minipage}
+\end{figure}
 
@@
 \subsection{Crime Discussion and Reported Crime}
-
-\begin{figure}[ht]
-    \includegraphics[width=\textwidth]{Images/BingAerial.jpg}
-    \caption{Aerial photograph of the Clock Tower, Peace Quad, and the Glenn G.
-Bartle Library Tower, June 16, 2009.
-This photograph was taken with a camera attached to a remote-controlled helicopter.}
-    \label{fig:fig-2}
-\end{figure}
 

### 2022-06-19 analysis/timeline.py
adding timeline code

@@ -1,0 +1,50 @@
+import sys
+import csv
+import datetime
+import psycopg2
+import os
+
+START_DATE = datetime.datetime(2022, 4, 6)
+NUMBER_OF_DAYS = 60
+
+conn = psycopg2.connect(
+    host=os.environ['PG_HOST'],
+    database=os.environ['PG_NAME'],
+    user=os.environ['PG_USERNAME'],
+    password=os.environ['PG_PASSWORD'],
+)
+
+print('connected to pg')
+
+cur = conn.cursor()
+
+date = START_DATE
+next_date = date + datetime.timedelta(days=1)
+sql = "select count(*) from posts where crawled_at >= %s and crawled_at < %s;"
+args = (date, next_date,)
+counts = []
+
+for i in range(NUMBER_OF_DAYS):
+    cur.execute(sql, args)
+    rows = cur.fetchall()
+
+    date += datetime.timedelta(days=1)
+    next_date = date + datetime.timedelta(days=1)
+
+    args = (date, next_date,)
+
+    for row in rows:
+        print(row[0])
+        counts.append(row[0])
+
+cur.close()
+
+date = START_DATE
+
+with open('timeline.csv', 'w', newline='') as csv_file:
+    writer = csv.writer(csv_file)
+    for c in counts:
+        if int(c) == 0:
+            break
+        writer.writerow([date, c])
+        date += datetime.timedelta(days=1)

### 2022-06-19 paper/main.tex
adding more figures

@@
 In total, 161,166 posts were gathered between April 5, 2022 and May 31, 2022.
-(REF - Figure of timeline).
+A timeline of this process can be seen in Figure \ref{fig:line-1}.
 The datastore archives posts in two formats.
@@
 
-(FIG)
+\begin{figure}[ht]
+    \includegraphics[width=\textwidth]{Images/timeline.png}
+    \caption{Map of crime discussion by MSA}
+    \label{fig:line-1}
+\end{figure}
 
@@
 
-\subsection{Activity}
+\subsection{Subreddit Activity}
 
@@
 
-\subsection{Crime Discussion and Population}
+\subsection{Population Demographics}
 
@@
 
-\subsection{Crime Discussion and Politics}
+\subsection{Political Atmosphere}
 
@@
     \caption{Perceived crime by political leaning}
+    \label{fig:scatter-1}
   \end{minipage}
@@
     \caption{Documented crime by political leaning}
+    \label{fig:scatter-2}
   \end{minipage}
@@
 
-\par Figure (REF) shows two scatterplots: one which shows the percent crime discussion in relation to politics among medium and large sized MSAs and the other which shows the documented crime rate among the same sample group in relation to politics.
+\par Figures \ref{fig:scatter-1} and \ref{fig:scatter-2} show two scatterplots: one which shows the percent crime discussion in relation to politics among medium and large sized MSAs and the other which shows the documented crime rate among the same sample group in relation to politics.
 The shades of the dots represent their political class.
@@
 
-\subsection{Crime Discussion and Reported Crime}
+\subsection{Reported Crime}
 

### 2022-06-20 paper/main.tex
more work on analysis

@@
     \includegraphics[width=\textwidth]{Images/timeline.png}
-    \caption{Map of crime discussion by MSA}
+    \caption{Number of daily posts across all subreddits}
     \label{fig:line-1}
@@
 
-\par Figure (REF) shows a cumulative distribution function of the data by population bucket.
-Here, we can see that the mean large population MSA has a fairly tight distribution, while the mean very small population MSA has a more spread out distribution.
+\par Figure \ref{fig:cdf-1} shows a cumulative distribution function of the data by population bucket.
+Here, we can see that the smallest value of the class of large populations is the greatest among the four classes, while its largest value is greater than all of the other classes' largest values.
+This relationship remains true throughout most of the distribution.
 
-(FIG)
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.75\textwidth]{Images/cdf.png}
+    \caption{Crime discussion by MSA population class}
+    \label{fig:cdf-1}
+\end{figure}
 
@@
     \includegraphics[width=\textwidth]{Images/pol.png}
-    \caption{Map of 2020 Presidential Election Results by MSA}
+    \caption{Map of 2020 presidential election results by MSA}
     \label{fig:map-2}
@@
     \includegraphics[width=0.75\textwidth]{Images/bar-politics.png}
-    \caption{Comparison of discussed crime and documented crime by politics}
+    \caption{Comparison of discussed crime and documented crime by political class}
     \label{fig:graph-2}
@@
 \subsection{Reported Crime}
+
+\par Another factor to consider alongside crime discussion is the reported crime rate of an MSA.
+Higher documented crime rates can lead to increased amounts of crime discussion, as crime may affect more members of the community.
+To measure MSA crime rates, we use the FBI's Uniform Crime Reporting Estimates (REF).
+The 384 Metropolitan Areas represent a differing level of crime rates, with a high of 1397.2 from Birmingham-Hoover, AL, a low of 44.3 from Bangor, ME, and an average of 380.9 among all MSAs.
+Table \ref{table:table-3} displays the MSAs with the ten highest documented crime rates.
+In this case, crime rates are defined as the amount of violent crime per 100,000 people.
+Additionally, the map in Figure \ref{fig:map-3} displays the crime rate for all Metropolitan Areas.
+
+\begin{table}[h!]
+    \centering
+    \small
+    \caption{Most active Metropolitan Areas per population}
+    %\begin{tabu} to 1.0\textwidth {| *{3}{c|} }
+    \begin{tabular}{| c | c | c |}
+    \hline
+    Metropolitan Statistical Area & Crime Rate & \% Crime Discussion\\ \hline
+    Birmingham-Hoover, AL & 1,397.2 & 2.52 \\ \hline
+    Farmington, NM & 1199.8 & 1.61 \\ \hline
+    Anchorage, AK & 1194.6 & 2.36 \\ \hline
+    Kansas City, MO-KS & 1159.4 & 3.16 \\ \hline
+    Memphis, TN-MS-AR & 1120.5 & 3.43 \\ \hline
+    Winston-Salem, NC & 1073.6 & 2.32 \\ \hline
+    Albuquerque, NM & 1043.4 & 4.53 \\ \hline
+    Danville, IL & 935.7 & 0.00 \\ \hline
+    Pine Bluff, AR & 895.4 & 12.5 \\ \hline
+    Odessa, TX & 881.8 & 4.30 \\ \hline
+	\end{tabular}
+	\label{table:table-4}
+\end{table}
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=\textwidth]{Images/Crime.png}
+    \caption{Reported Crime Rate by MSA}
+    \label{fig:map-3}
+\end{figure}
+
+\par From Tables \ref{table:table-3} and \ref{table:table-4}, as well as Figures \ref{fig:map-1} and \ref{fig:map-3}, we can see that MSAs with high reported crime rates do not necessarily have high amounts of crime discussion.
+The same goes for MSAs with low crime rates and low amounts of crime discussion.
+Based on the data, crime rate does not seem to have an effect on the level of crime discussion in a community.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=\textwidth]{Images/diff.png}
+    \caption{Reported Crime Rate by MSA}
+    \label{fig:map-4}
+\end{figure}
+
+\par Many Metropolitan Areas with high documented crime rates lie in the South and Midwest (REF).
+However, many these MSAs have low amounts of crime discussion.
+To calculate the discrepancies between crime discussion and reported crime, we calculate the difference between the min-max normalized crime discussion score and the min-maxed documented crime score.
+Figure \ref{fig:map-4} maps this normalized difference score.
+Higher positive values indicate that the amount of crime discussion is higher than actual crime, while lower negative values indicate that actual crime is higher than crime discussion.
+MSAs in which the ratio of crime discussion and documented crime are roughly equal rest around a score of zero.
+
+\par Table \ref{table:table-5} displays the 15 highest and lowest scoring MSAs for the crime discussion to crime rate ratio.
+A full listing can be found in Appendix (REF).
+Of the highest scoring MSAs, large and very small Metropolitan Areas are over-represented, while all population sizes are represented among the lowest scoring Metropolitan Areas.
+When considering political affiliation, very liberal cities represent 33\% of the highest scoring MSAs while only consisting of 10\% of the total number of Metropolitan Areas.
+For the lowest scoring MSAs, conservative and very conservative Metropolitan Areas represent 80\% of the lowest scoring members while only making up 56\% of the total number of members.
+
+\begin{table}[h!]
+    \centering
+    \caption{General formatting requirements for thesis or dissertation}
+    %\begin{tabu} to 1.0\textwidth {| *{3}{c|} }
+    \begin{tabular}{| c | c | c | c |}
+    \hline
+    \multicolumn{2}{|c|}{Higher Score} & \multicolumn{2}{|c|}{Lower Score} \\ \hline
+    Metropolitan Area & Score & Metropolitan Area & Score \\ \hline
+    Seattle-Tacoma-Bellevue, WA & 0.743 & Birmingham-Hoover, AL & -0.861 \\ \hline
+    Lewiston, ME & 0.723 & Farmington, NM & -0.770 \\ \hline
+    Lewiston, ID-WA & 0.614 & Anchorage, AK & -0.725 \\ \hline
+    Bay City, MI & 0.496 & Danville, IL & -0.670 \\ \hline
+    Portland, OR-WA & 0.409 & Kansas City, MO-KS & -0.656 \\ \hline
+    Decatur, AL & 0.381 & Winston-Salem, NC & -0.641 \\ \hline
+    New York, NY-NJ-PA & 0.352 & Memphis, TN-MS-AR & -0.613 \\ \hline
+    Anniston, AL & 0.344 & Monroe, LA & -0.582 \\ \hline
+    Rocky Mount, NC & 0.323 & Carbondale, IL & -0.501 \\ \hline
+    Los Angeles, CA & 0.319 & Albuquerque, NM & -0.497 \\ \hline
+    St. Cloud, MN & 0.308 & Fairbanks, AK & -0.490 \\ \hline
+    Burlington, VT & 0.290 & Lubbock, TX & -0.489 \\ \hline
+    Binghamton, NY & 0.273 & Corpus Christi, TX & -0.448 \\ \hline
+    Muncie, IN & 0.262 & Jackson, TN & -0.439 \\ \hline
+    Sheboygan, WI & 0.238 & Dothan, AL & -0.431 \\ \hline
+	\end{tabular}
+	\label{table:table-5}
+\end{table}
 

### 2022-06-23 paper/main.tex
updated analysis

@@
 
+TODO: User Scraper stuff
+
 \subsection{Contextual Data}
 \par A variety of data were utilized to highlight trends in the Reddit posts.
-One variable that subreddits are compared to is population size of the MSA (REF).
+One variable that subreddits are compared to is population size of the MSA.
 These values range from a minimum of 58,639 (Carson City, NV) and a maximum of 20,140,470 (New York-Newark-Jersey City, NY-NJ-PA).
@@
 \par The most active MSAs by total number of posts share some common, predictable traits.
-First, all of the Metropolitan Areas listed have populations above 1,000,000.
-While expected, some notable MSAs were not included, such as New York-Newark-Jersey City, NJ-NJ-PA and Los Angeles-Long Beach-Anaheim, CA, which have populations of 20,140,470 and 13,200,998, respectfully.
-One possible explanation for these discrepancies is the fact that there is no uniform, consistent moderation policy among subreddits (REF).
+One shared characteristic is that all of the Metropolitan Areas listed have populations above 1,000,000.
+While expected, some of the most notable MSAs were not included, such as New York-Newark-Jersey City, NJ-NJ-PA and Los Angeles-Long Beach-Anaheim, CA, which have populations of 20,140,470 and 13,200,998, respectfully.
+One possible explanation for these exclusions is the fact that there is no uniform, consistent moderation policy among subreddits (REF).
 For example, some subreddits automatically filter out all posts and manually approve them, or they disallow certain types of posts (REF - nyc n chicago rules).
+Subreddits with more laissez-faire moderation policies will have more posts simply because they are not removing a mass of posts that could be considered redundant or irrelevant.
 
@@
 
-\par The list of most active MSAs when accounting for population also have some common traits.
+\par The list of most active MSAs when normalizing by population also share some common traits.
 These MSAs are generally politically liberal (REF) and have large college age populations (REF).
-These areas have large populations of people that fall under Reddit's main demographic (REF) and, as a result, have correspondingly active communities.
+Essentially, these areas have large populations of people that fall under Reddit's main demographic (REF) and, as a result, have correspondingly active communities.
 
@@
 
-\par Figure \ref{fig:graph-1} provides average normalized scores for documented crime to compare trends to crime discussion.
-We can see that as population increases, documented crime rates gradually increase.
+\par From Figure \ref{fig:graph-1}, we can see that as population increases, documented crime rates gradually increase.
 This trend is semi-reflected in the crime discussion data.
 Crime discussion scores are roughly equivalent for the very small, small, and medium buckets.
-However, the large population bucket has a significantly higher crime discussion score than the other buckets.
+However, the large population bucket has a significantly higher crime discussion score than that of the other buckets.
 The large population bucket has a 6\% greater score than the medium population bucket when comparing documented crime data, but the large population bucket has a 56\% greater score than the medium population bucket when comparing crime discussion data.
@@
 Here, we can see that the smallest value of the class of large populations is the greatest among the four classes, while its largest value is greater than all of the other classes' largest values.
-This relationship remains true throughout most of the distribution.
+This relationship remains true throughout most of the distribution, resulting in the large MSAs having the highest mean crime discussion score.
+When looking at the very small MSAs, we can see that some Metropolitan Areas in its category have high average crime discussion.
+However, a significant amount of very small MSAs have no crime discussion at all.
+From the CDF we can see that almost 20\% of very small MSA subreddits have not discussed crime at all.
+The next highest zero crime discussion class is small, with about 8\% of communities not discussing crime.
 
@@
 
+\par When looking back at the map of crime discussion in Figure \ref{fig:map-1}, we can see that the Metropolitan Areas with the most crime discussion are not bound by population size.
+MSAs both small and large are represented.
+However, this trend is not reflected among Metropolitan Areas with the least amount of crime discussion.
+These areas are almost exclusively in the very small and small population buckets, with no large population MSAs being represented.
+Having at least some degree of crime discussion in all MSAs and significant representation in the highest scoring MSAs leads to large population Metropolitan Areas scoring the greatest average crime discussion among all population classes.
+
 \subsection{Political Atmosphere}
@@
 To measure this, we look at the results of the 2020 presidential election.
-We consider the number of votes that the Democratic and Republic parties received as stand-ins for liberal and conservative political views, respectfully.
+We consider the number of votes that the Democratic and Republican parties received as stand-ins for liberal and conservative political views, respectfully.
 Political affiliation of the 384 MSAs is broken down into the five categories discussed earlier: very conservative, conservative, moderate, liberal, and very liberal.
@@
 
-\par In identifying trends based on politics, we follow a familiar method and take the mean crime discussion value of each political class.
+\par In identifying trends based on politics, we follow a familiar method; we take the mean normalized crime discussion value and mean normalized documented crime rate of each political class.
 Figure \ref{fig:graph-2} displays the average min-max normalization score for crime discussion and reported crime for each political class.
@@
 
-\par When looking at crime discussion rates, we can see that more liberal cities have the highest rates of crime discussion.
-The very liberal class has a 32\% higher crime discussion score than the next largest value.
-The two conservative political classes have the lowest crime discussion scores.
+\par When looking at Figure \ref{fig:graph-2}, we can see that among crime discussion rates, more liberal cities have the highest average scores.
+As the share of democratic voters increase, the average crime discussion score increases, with moderate MSAs scoring slightly higher than liberal MSAs.
+The very liberal class has a 32\% higher crime discussion score than the next largest score.
+Additionally, the two conservative political classes have the lowest mean crime discussion scores.
 However, these trends are not reflected in the documented crime rate scores.
-Figure \ref{fig:graph-2} shows that very liberal MSAs have a lower mean documented crime rate than more conservative areas.
-Very liberal areas are also the only class in which the crime discussion score is higher than the reported crime rate score.
+Figure \ref{fig:graph-2} shows that very liberal MSAs have a lower mean documented crime rate than more conservative areas, as well as the lowest mean score overall.
+Very liberal areas are also the only class in which the crime discussion score is higher than the reported crime rate score despite its low average documented crime.
 
@@
 MSAs that lean conservative, such as Birmingham-Hoover, AL and Kansas City, MO-KS have among the highest crime rates, as well as more politically moderate cities, such as Memphis, TN-MS-AR.
+
+\par When considering the data, we can see a strong relationship between how liberal a Metropolitan Area votes to how high its average crime discussion lies.
+Despite having lower than average documented crime, very liberal Metropolitan Areas have the highest crime discussion rates.
 
@@
 
+\par Table \ref{table:table-4} represents a diverse group of Metropolitan Areas in regards to population, politics, and crime discussion rates.
+Populations range from very small MSAs to large MSAs.
+Most of the MSAs lean conservative, but there are some liberal cities included, such as Albuquerque, NM.
+Additionally, a wide array of crime discussion percentages are noted, including Danville, IL at a low of 0\% and Pine Bluff, AR at a high of 12.5\%.
+
 \begin{figure}[ht]
@@
 \par From Tables \ref{table:table-3} and \ref{table:table-4}, as well as Figures \ref{fig:map-1} and \ref{fig:map-3}, we can see that MSAs with high reported crime rates do not necessarily have high amounts of crime discussion.
+This includes Metropolitan Areas such as Danville, IL and Farmington, NM.
 The same goes for MSAs with low crime rates and low amounts of crime discussion.
-Based on the data, crime rate does not seem to have an effect on the level of crime discussion in a community.
+New York-Newark-Jersey City, NY-NJ-PA and Seattle-Tacoma-Bellevue, WA have significantly higher normalized crime discussion rates than normalized documented crime rates.
 
@@
 
-\par Many Metropolitan Areas with high documented crime rates lie in the South and Midwest (REF).
+\par From the map in Figure \ref{fig:map-3}, we can see that many Metropolitan Areas with high documented crime rates lie in the South and Midwest (REF).
 However, many these MSAs have low amounts of crime discussion.
@@
 \end{table}
+
+\par When considering the documented crime data, we can see that high documented crime rates do not necessarily lead to high crime discussion rates, and vice versa.
+Figure \ref{fig:map-4} and Table \ref{table:table-5} show that more liberal and larger MSAs in the Northeast and on the West Coast have higher rates of crime discussion than crime rates, while smaller, more conservative MSAs in the South and Midwest have higher crime rates than crime discussion.
+As a result of these differing scores, no relationship between crime discussion and reported crime rates emerges.
 

### 2022-06-24 paper/main.tex
added conclusion

@@
 
-\chapter{Subreddit-level Analysis}
+\chapter{Analysis}
 
@@
 
-\section{Results}
+\section{Raw Results}
 
@@
 \end{figure}
+
+\section{Contextual Analysis}
 
@@
 
-\chapter{User-level Analysis}
-\par TODO
+\section{Sentiment Analysis}
 
-\section{Data Overview}
-\par TODO: talk about sample of users and their data
-
-\section{Methods}
-\par TODO: talk about code design
-
-\section{Results}
-\par TODO: discuss results
+TODO
 
 \chapter{Conclusion}
+
+\par We have discussed the nature and prevalence of crime discussion on Reddit, a social media website, as it pertains to location-based communities.
+To obtain the necessary data and information, we have created a highly available Reddit scraper that fetches all posts from communities that represent the 384 Metropolitan Statistical Areas of the United States.
+The scraper gathered 161,166 posts over a two-month time span.
+Of these 161,166 posts, a total of 6,792 were determined to discuss crime.
+
+\par Through analysis of user-submitted posts, we have found that communities that represent larger Metropolitan Statistical Areas and more liberal Metropolitan Statistical Areas tend to have higher rates of crime discussion.
+However, there is no correlation between high documented crime rates and high crime discussion rates.
+Furthermore, we have found that the users that make submissions about crime are significantly more negative in their posting and commenting style than those that post about non-crime topics.
+
+\par This paper presents an alternative approach to the measurement of crime discussion and media.
+While there have been several notable papers examining the relationship between crime discussion and traditional media, few have bridged the gap between media, such as newspapers and television stations, and modern social media networks, such as Reddit.
+
+\par While this paper provides a first look at the crime discussion dynamics on Reddit, there are several paths that continued research could explore.
+One pathway of future work on the relationship between crime discussion and social media can include a more in-depth analysis of users that post about crime.
+By delving deep into these users' posting histories, we can attempt to determine if there is any sort of coordinated effort to push crime discussion in certain communities.
+Another approach could be applying the tool and analysis used on Reddit to other social media platforms, such as Facebook or Nextdoor, to determine if this phenomenon is Reddit-specific.
 
@@
 
-% Appendix A - Metro, subreddit, population, hits
+% Appendix A - Metro, subreddit
 % Appendix B - Metro, population, pop class, Pcrime rate

### 2022-06-24 paper/main.tex
added appendix a

@@
 \usepackage{geometry}
+\usepackage{longtable}
 
@@
 
+\begin{longtable}{| p{.6\textwidth} | p{.15\textwidth} | p{.15\textwidth} |}
+    %\begin{tabu} to 1.0\textwidth {| *{3}{c|} }
+    \hline
+    Metropolitan Statistical Area & \% Crime Posts & Diff. Score \\ \hline
+    Abilene, TX Metro Area & 1.27 & -0.16 \\ \hline
+    Akron, OH Metro Area & 2.34 & -0.14 \\ \hline
+    Albany, GA Metro Area & 3.39 & -0.33 \\ \hline
+    Albany-Lebanon, OR Metro Area & 1.67 & -0.01 \\ \hline
+    Albany-Schenectady-Troy, NY Metro Area & 2.48 & -0.05 \\ \hline
+    Albuquerque, NM Metro Area & 4.53 & -0.5 \\ \hline
+    Alexandria, LA Metro Area & 8.82 & -0.12 \\ \hline
+    Allentown-Bethlehem-Easton, PA-NJ Metro Area & 2.46 & 0.02 \\ \hline
+    Altoona, PA Metro Area & 3.45 & -0.05 \\ \hline
+    Amarillo, TX Metro Area & 6.6 & -0.06 \\ \hline
+    Ames, IA Metro Area & 4.55 & 0.11 \\ \hline
+    Anchorage, AK Metro Area & 2.36 & -0.73 \\ \hline
+    Ann Arbor, MI Metro Area & 1.2 & -0.19 \\ \hline
+    Anniston-Oxford, AL Metro Area & 15.69 & 0.34 \\ \hline
+    Appleton, WI Metro Area & 1.53 & -0.03 \\ \hline
+    Asheville, NC Metro Area & 3.35 & -0.04 \\ \hline
+    Athens-Clarke County, GA Metro Area & 1.95 & -0.11 \\ \hline
+    Atlanta-Sandy Springs-Alpharetta, GA Metro Area & 5.73 & 0.09 \\ \hline
+    Atlantic City-Hammonton, NJ Metro Area & 1.54 & -0.1 \\ \hline
+    Auburn-Opelika, AL Metro Area & 4.35 & -0.13 \\ \hline
+    Augusta-Richmond County, GA-SC Metro Area & 0.93 & -0.21 \\ \hline
+    Austin-Round Rock-Georgetown, TX Metro Area & 3.62 & -0.01 \\ \hline
+    Bakersfield, CA Metro Area & 5.68 & -0.13 \\ \hline
+    Baltimore-Columbia-Towson, MD Metro Area & 4.18 & -0.27 \\ \hline
+    Bangor, ME Metro Area & 1.47 & 0.05 \\ \hline
+    Barnstable Town, MA Metro Area & 1.84 & -0.13 \\ \hline
+    Baton Rouge, LA Metro Area & 6.34 & -0.05 \\ \hline
+    Battle Creek, MI Metro Area & 4.88 & -0.18 \\ \hline
+    Bay City, MI Metro Area & 14.0 & 0.5 \\ \hline
+    Beaumont-Port Arthur, TX Metro Area & 5.94 & -0.06 \\ \hline
+    Beckley, WV Metro Area & 0.0 & -0.24 \\ \hline
+    Bellingham, WA Metro Area & 4.06 & 0.07 \\ \hline
+    Bend, OR Metro Area & 2.88 & 0.04 \\ \hline
+    Billings, MT Metro Area & 1.54 & -0.3 \\ \hline
+    Binghamton, NY Metro Area & 8.68 & 0.27 \\ \hline
+    Birmingham-Hoover, AL Metro Area & 2.53 & -0.86 \\ \hline
+    Bismarck, ND Metro Area & 0.0 & -0.22 \\ \hline
+    Blacksburg-Christiansburg, VA Metro Area & 6.67 & 0.23 \\ \hline
+    Bloomington, IL Metro Area & 1.63 & -0.16 \\ \hline
+    Bloomington, IN Metro Area & 3.38 & -0.07 \\ \hline
+    Bloomsburg-Berwick, PA Metro Area & 1.89 & -0.03 \\ \hline
+    Boise City, ID Metro Area & 2.66 & -0.03 \\ \hline
+    Boston-Cambridge-Newton, MA-NH Metro Area & 4.36 & 0.04 \\ \hline
+    Boulder, CO Metro Area & 4.37 & 0.05 \\ \hline
+    Bowling Green, KY Metro Area & 3.7 & 0.09 \\ \hline
+    Bremerton-Silverdale-Port Orchard, WA Metro Area & 4.11 & 0.04 \\ \hline
+    Bridgeport-Stamford-Norwalk, CT Metro Area & 1.39 & -0.05 \\ \hline
+    Brownsville-Harlingen, TX Metro Area & 3.19 & -0.09 \\ \hline
+    Brunswick, GA Metro Area & 7.14 & 0.13 \\ \hline
+    Buffalo-Cheektowaga, NY Metro Area & 8.3 & 0.2 \\ \hline
+    Burlington, NC Metro Area & 4.0 & -0.07 \\ \hline
+    Burlington-South Burlington, VT Metro Area & 7.88 & 0.29 \\ \hline
+    California-Lexington Park, MD Metro Area & 1.23 & -0.08 \\ \hline
+    Canton-Massillon, OH Metro Area & 2.67 & -0.1 \\ \hline
+    Cape Coral-Fort Myers, FL Metro Area & 5.17 & 0.1 \\ \hline
+    Cape Girardeau, MO-IL Metro Area & 2.94 & -0.11 \\ \hline
+    Carbondale-Marion, IL Metro Area & 1.61 & -0.5 \\ \hline
+    Carson City, NV Metro Area & 1.25 & -0.18 \\ \hline
+    Casper, WY Metro Area & 7.14 & 0.19 \\ \hline
+    Cedar Rapids, IA Metro Area & 4.86 & 0.13 \\ \hline
+    Chambersburg-Waynesboro, PA Metro Area & 0.0 & -0.12 \\ \hline
+    Champaign-Urbana, IL Metro Area & 0.0 & -0.35 \\ \hline
+    Charleston, WV Metro Area & 3.17 & -0.15 \\ \hline
+    Charleston-North Charleston, SC Metro Area & 1.94 & -0.18 \\ \hline
+    Charlotte-Concord-Gastonia, NC-SC Metro Area & 2.75 & -0.15 \\ \hline
+    Charlottesville, VA Metro Area & 2.35 & 0.0 \\ \hline
+    Chattanooga, TN-GA Metro Area & 3.25 & -0.2 \\ \hline
+    Cheyenne, WY Metro Area & 7.36 & 0.19 \\ \hline
+    Chicago-Naperville-Elgin, IL-IN-WI Metro Area & 4.86 & -0.1 \\ \hline
+    Chico, CA Metro Area & 6.52 & 0.04 \\ \hline
+    Cincinnati, OH-KY-IN Metro Area & 3.25 & 0.01 \\ \hline
+    Clarksville, TN-KY Metro Area & 1.34 & -0.2 \\ \hline
+    Cleveland, TN Metro Area & 3.33 & -0.22 \\ \hline
+    Cleveland-Elyria, OH Metro Area & 2.56 & -0.15 \\ \hline
+    Coeur d'Alene, ID Metro Area & 1.55 & -0.07 \\ \hline
+    College Station-Bryan, TX Metro Area & 2.58 & -0.05 \\ \hline
+    Colorado Springs, CO Metro Area & 2.5 & -0.2 \\ \hline
+    Columbia, MO Metro Area & 0.75 & -0.15 \\ \hline
+    Columbia, SC Metro Area & 4.29 & -0.18 \\ \hline
+    Columbus, GA-AL Metro Area & 2.58 & -0.24 \\ \hline
+    Columbus, IN Metro Area & 1.49 & -0.02 \\ \hline
+    Columbus, OH Metro Area & 2.57 & -0.06 \\ \hline
+    Corpus Christi, TX Metro Area & 1.44 & -0.45 \\ \hline
+    Corvallis, OR Metro Area & 4.03 & 0.11 \\ \hline
+    Crestview-Fort Walton Beach-Destin, FL Metro Area & 1.38 & -0.15 \\ \hline
+    Cumberland, MD-WV Metro Area & 2.08 & -0.08 \\ \hline
+    Dallas-Fort Worth-Arlington, TX Metro Area & 5.45 & 0.05 \\ \hline
+    Dalton, GA Metro Area & 1.15 & -0.08 \\ \hline
+    Danville, IL Metro Area & 0.0 & -0.67 \\ \hline
+    Daphne-Fairhope-Foley, AL Metro Area & 0.0 & -0.19 \\ \hline
+    Davenport-Moline-Rock Island, IA-IL Metro Area & 2.16 & -0.14 \\ \hline
+    Dayton-Kettering, OH Metro Area & 1.83 & -0.13 \\ \hline
+    Decatur, AL Metro Area & 10.94 & 0.38 \\ \hline
+    Decatur, IL Metro Area & 0.0 & -0.3 \\ \hline
+    Deltona-Daytona Beach-Ormond Beach, FL Metro Area & 2.13 & -0.11 \\ \hline
+    Denver-Aurora-Lakewood, CO Metro Area & 5.67 & 0.02 \\ \hline
+    Des Moines-West Des Moines, IA Metro Area & 4.06 & -0.29 \\ \hline
+    Detroit-Warren-Dearborn, MI Metro Area & 3.6 & -0.17 \\ \hline
+    Dothan, AL Metro Area & 0.0 & -0.43 \\ \hline
+    Dover, DE Metro Area & 0.0 & -0.31 \\ \hline
+    Dubuque, IA Metro Area & 1.27 & -0.03 \\ \hline
+    Duluth, MN-WI Metro Area & 0.62 & -0.12 \\ \hline
+    Durham-Chapel Hill, NC Metro Area & 2.23 & -0.19 \\ \hline
+    East Stroudsburg, PA Metro Area & 6.25 & 0.17 \\ \hline
+    Eau Claire, WI Metro Area & 4.55 & 0.1 \\ \hline
+    El Centro, CA Metro Area & 1.92 & -0.14 \\ \hline
+    El Paso, TX Metro Area & 3.09 & -0.07 \\ \hline
+    Elizabethtown-Fort Knox, KY Metro Area & 1.92 & 0.03 \\ \hline
+    Elkhart-Goshen, IN Metro Area & 4.92 & -0.29 \\ \hline
+    Elmira, NY Metro Area & 1.96 & -0.05 \\ \hline
+    Enid, OK Metro Area & 5.26 & 0.02 \\ \hline
+    Erie, PA Metro Area & 3.36 & -0.03 \\ \hline
+    Eugene-Springfield, OR Metro Area & 3.97 & 0.05 \\ \hline
+    Evansville, IN-KY Metro Area & 1.12 & -0.17 \\ \hline
+    Fairbanks, AK Metro Area & 1.42 & -0.49 \\ \hline
+    Fargo, ND-MN Metro Area & 2.77 & -0.06 \\ \hline
+    Farmington, NM Metro Area & 1.61 & -0.77 \\ \hline
+    Fayetteville, NC Metro Area & 4.07 & -0.4 \\ \hline
+    Fayetteville-Springdale-Rogers, AR Metro Area & 2.44 & -0.14 \\ \hline
+    Flagstaff, AZ Metro Area & 1.07 & -0.27 \\ \hline
+    Flint, MI Metro Area & 9.71 & 0.12 \\ \hline
+    Florence, SC Metro Area & 3.51 & -0.4 \\ \hline
+    Florence-Muscle Shoals, AL Metro Area & 6.45 & 0.14 \\ \hline
+    Fond du Lac, WI Metro Area & 0.0 & -0.13 \\ \hline
+    Fort Collins, CO Metro Area & 3.0 & -0.0 \\ \hline
+    Fort Smith, AR-OK Metro Area & 1.52 & -0.34 \\ \hline
+    Fort Wayne, IN Metro Area & 2.44 & -0.08 \\ \hline
+    Fresno, CA Metro Area & 1.88 & -0.32 \\ \hline
+    Gadsden, AL Metro Area & 2.04 & -0.27 \\ \hline
+    Gainesville, FL Metro Area & 2.57 & -0.35 \\ \hline
+    Gainesville, GA Metro Area & 1.61 & -0.06 \\ \hline
+    Gettysburg, PA Metro Area & 2.86 & 0.06 \\ \hline
+    Glens Falls, NY Metro Area & 5.08 & 0.19 \\ \hline
+    Goldsboro, NC Metro Area & 0.0 & -0.3 \\ \hline
+    Grand Forks, ND-MN Metro Area & 1.32 & -0.11 \\ \hline
+    Grand Island, NE Metro Area & 0.0 & -0.27 \\ \hline
+    Grand Junction, CO Metro Area & 4.32 & 0.03 \\ \hline
+    Grand Rapids-Kentwood, MI Metro Area & 5.08 & 0.05 \\ \hline
+    Grants Pass, OR Metro Area & 7.25 & 0.23 \\ \hline
+    Great Falls, MT Metro Area & 7.69 & 0.17 \\ \hline
+    Greeley, CO Metro Area & 6.38 & 0.2 \\ \hline
+    Green Bay, WI Metro Area & 3.62 & 0.04 \\ \hline
+    Greensboro-High Point, NC Metro Area & 2.38 & -0.25 \\ \hline
+    Greenville, NC Metro Area & 2.06 & -0.15 \\ \hline
+    Greenville-Anderson, SC Metro Area & 1.36 & -0.27 \\ \hline
+    Gulfport-Biloxi, MS Metro Area & 1.15 & -0.1 \\ \hline
+    Hagerstown-Martinsburg, MD-WV Metro Area & 3.41 & -0.01 \\ \hline
+    Hammond, LA Metro Area & 5.56 & -0.3 \\ \hline
+    Hanford-Corcoran, CA Metro Area & 4.0 & -0.14 \\ \hline
+    Harrisburg-Carlisle, PA Metro Area & 1.38 & -0.11 \\ \hline
+    Harrisonburg, VA Metro Area & 3.72 & 0.11 \\ \hline
+    Hartford-East Hartford-Middletown, CT Metro Area & 2.27 & -0.02 \\ \hline
+    Hattiesburg, MS Metro Area & 0.0 & -0.17 \\ \hline
+    Hickory-Lenoir-Morganton, NC Metro Area & 3.57 & -0.11 \\ \hline
+    Hilton Head Island-Bluffton, SC Metro Area & 0.0 & -0.28 \\ \hline
+    Hinesville, GA Metro Area & 0.0 & -0.3 \\ \hline
+    Homosassa Springs, FL Metro Area & 0.0 & -0.18 \\ \hline
+    Hot Springs, AR Metro Area & 1.98 & -0.27 \\ \hline
+    Houma-Thibodaux, LA Metro Area & 3.51 & -0.07 \\ \hline
+    Houston-The Woodlands-Sugar Land, TX Metro Area & 5.02 & -0.15 \\ \hline
+    Huntington-Ashland, WV-KY-OH Metro Area & 4.11 & 0.04 \\ \hline
+    Huntsville, AL Metro Area & 1.94 & -0.29 \\ \hline
+    Idaho Falls, ID Metro Area & 4.26 & 0.09 \\ \hline
+    Indianapolis-Carmel-Anderson, IN Metro Area & 4.19 & -0.23 \\ \hline
+    Iowa City, IA Metro Area & 2.98 & -0.03 \\ \hline
+    Ithaca, NY Metro Area & 2.68 & 0.06 \\ \hline
+    Jackson, MI Metro Area & 4.0 & -0.15 \\ \hline
+    Jackson, MS Metro Area & 3.37 & -0.06 \\ \hline
+    Jackson, TN Metro Area & 0.0 & -0.44 \\ \hline
+    Jacksonville, FL Metro Area & 2.48 & -0.2 \\ \hline
+    Jacksonville, NC Metro Area & 1.85 & -0.09 \\ \hline
+    Janesville-Beloit, WI Metro Area & 5.17 & 0.12 \\ \hline
+    Jefferson City, MO Metro Area & 0.0 & -0.16 \\ \hline
+    Johnson City, TN Metro Area & 2.13 & -0.12 \\ \hline
+    Johnstown, PA Metro Area & 7.14 & 0.2 \\ \hline
+    Jonesboro, AR Metro Area & 2.0 & -0.29 \\ \hline
+    Joplin, MO Metro Area & 4.17 & -0.01 \\ \hline
+    Kahului-Wailuku-Lahaina, HI Metro Area & 0.98 & -0.14 \\ \hline
+    Kalamazoo-Portage, MI Metro Area & 2.55 & -0.27 \\ \hline
+    Kankakee, IL Metro Area & 1.89 & -0.17 \\ \hline
+    Kansas City, MO-KS Metro Area & 3.16 & -0.66 \\ \hline
+    Kennewick-Richland, WA Metro Area & 3.94 & 0.06 \\ \hline
+    Killeen-Temple, TX Metro Area & 5.68 & 0.12 \\ \hline
+    Kingsport-Bristol, TN-VA Metro Area & 6.15 & 0.12 \\ \hline
+    Kingston, NY Metro Area & 1.92 & -0.0 \\ \hline
+    Knoxville, TN Metro Area & 2.78 & -0.1 \\ \hline
+    Kokomo, IN Metro Area & 6.45 & -0.04 \\ \hline
+    La Crosse-Onalaska, WI-MN Metro Area & 4.9 & 0.18 \\ \hline
+    Lafayette, LA Metro Area & 6.12 & 0.0 \\ \hline
+    Lafayette-West Lafayette, IN Metro Area & 2.75 & -0.01 \\ \hline
+    Lake Charles, LA Metro Area & 2.08 & -0.28 \\ \hline
+    Lake Havasu City-Kingman, AZ Metro Area & 1.96 & -0.06 \\ \hline
+    Lakeland-Winter Haven, FL Metro Area & 2.94 & -0.04 \\ \hline
+    Lancaster, PA Metro Area & 1.96 & -0.02 \\ \hline
+    Lansing-East Lansing, MI Metro Area & 4.79 & -0.04 \\ \hline
+    Laredo, TX Metro Area & 0.0 & -0.23 \\ \hline
+    Las Cruces, NM Metro Area & 5.53 & -0.09 \\ \hline
+    Las Vegas-Henderson-Paradise, NV Metro Area & 2.32 & -0.25 \\ \hline
+    Lawrence, KS Metro Area & 3.67 & -0.08 \\ \hline
+    Lawton, OK Metro Area & 1.82 & -0.41 \\ \hline
+    Lebanon, PA Metro Area & 0.0 & -0.12 \\ \hline
+    Lewiston, ID-WA Metro Area & 12.96 & 0.61 \\ \hline
+    Lewiston-Auburn, ME Metro Area & 15.38 & 0.72 \\ \hline
+    Lexington-Fayette, KY Metro Area & 2.02 & -0.05 \\ \hline
+    Lima, OH Metro Area & 4.0 & -0.01 \\ \hline
+    Lincoln, NE Metro Area & 3.05 & -0.08 \\ \hline
+    Little Rock-North Little Rock-Conway, AR Metro Area & 7.08 & -0.17 \\ \hline
+    Logan, UT-ID Metro Area & 3.42 & 0.1 \\ \hline
+    Longview, TX Metro Area & 1.49 & -0.15 \\ \hline
+    Longview, WA Metro Area & 5.36 & 0.16 \\ \hline
+    Los Angeles-Long Beach-Anaheim, CA Metro Area & 12.0 & 0.32 \\ \hline
+    Louisville/Jefferson County, KY-IN Metro Area & 4.4 & -0.07 \\ \hline
+    Lubbock, TX Metro Area & 2.02 & -0.49 \\ \hline
+    Lynchburg, VA Metro Area & 2.7 & -0.02 \\ \hline
+    Macon-Bibb County, GA Metro Area & 2.88 & -0.17 \\ \hline
+    Madera, CA Metro Area & 0.0 & -0.38 \\ \hline
+    Madison, WI Metro Area & 3.79 & 0.05 \\ \hline
+    Manchester-Nashua, NH Metro Area & 1.23 & -0.1 \\ \hline
+    Manhattan, KS Metro Area & 4.05 & -0.09 \\ \hline
+    Mankato, MN Metro Area & 0.0 & -0.13 \\ \hline
+    Mansfield, OH Metro Area & 0.0 & -0.16 \\ \hline
+    McAllen-Edinburg-Mission, TX Metro Area & 3.26 & -0.01 \\ \hline
+    Medford, OR Metro Area & 6.74 & 0.13 \\ \hline
+    Memphis, TN-MS-AR Metro Area & 3.43 & -0.61 \\ \hline
+    Merced, CA Metro Area & 4.29 & -0.16 \\ \hline
+    Miami-Fort Lauderdale-Pompano Beach, FL Metro Area & 3.28 & -0.12 \\ \hline
+    Michigan City-La Porte, IN Metro Area & 1.1 & -0.23 \\ \hline
+    Midland, MI Metro Area & 3.08 & 0.07 \\ \hline
+    Midland, TX Metro Area & 4.3 & 0.01 \\ \hline
+    Milwaukee-Waukesha, WI Metro Area & 4.09 & -0.19 \\ \hline
+    Minneapolis-St. Paul-Bloomington, MN-WI Metro Area & 5.87 & 0.13 \\ \hline
+    Missoula, MT Metro Area & 2.45 & -0.12 \\ \hline
+    Mobile, AL Metro Area & 2.79 & -0.22 \\ \hline
+    Modesto, CA Metro Area & 2.76 & -0.23 \\ \hline
+    Monroe, LA Metro Area & 0.0 & -0.58 \\ \hline
+    Monroe, MI Metro Area & 3.28 & -0.01 \\ \hline
+    Montgomery, AL Metro Area & 2.36 & -0.2 \\ \hline
+    Morgantown, WV Metro Area & 0.95 & -0.09 \\ \hline
+    Morristown, TN Metro Area & 9.3 & 0.23 \\ \hline
+    Mount Vernon-Anacortes, WA Metro Area & 3.66 & 0.09 \\ \hline
+    Muncie, IN Metro Area & 7.94 & 0.26 \\ \hline
+    Muskegon, MI Metro Area & 7.21 & 0.07 \\ \hline
+    Myrtle Beach-Conway-North Myrtle Beach, SC-NC Metro Area & 1.74 & -0.16 \\ \hline
+    Napa, CA Metro Area & 4.72 & -0.13 \\ \hline
+    Naples-Marco Island, FL Metro Area & 3.72 & 0.04 \\ \hline
+    Nashville-Davidson--Murfreesboro--Franklin, TN Metro Area & 3.76 & -0.2 \\ \hline
+    New Bern, NC Metro Area & 0.0 & -0.2 \\ \hline
+    New Haven-Milford, CT Metro Area & 2.57 & -0.05 \\ \hline
+    New Orleans-Metairie, LA Metro Area & 5.29 & -0.1 \\ \hline
+    New York-Newark-Jersey City, NY-NJ-PA Metro Area & 10.72 & 0.35 \\ \hline
+    Niles, MI Metro Area & 4.08 & -0.17 \\ \hline
+    North Port-Sarasota-Bradenton, FL Metro Area & 2.38 & -0.1 \\ \hline
+    Norwich-New London, CT Metro Area & 6.48 & 0.22 \\ \hline
+    Ocala, FL Metro Area & 2.42 & -0.18 \\ \hline
+    Ocean City, NJ Metro Area & 1.67 & -0.03 \\ \hline
+    Odessa, TX Metro Area & 4.3 & -0.39 \\ \hline
+    Ogden-Clearfield, UT Metro Area & 1.75 & -0.03 \\ \hline
+    Oklahoma City, OK Metro Area & 3.17 & -0.16 \\ \hline
+    Olympia-Lacey-Tumwater, WA Metro Area & 3.54 & 0.02 \\ \hline
+    Omaha-Council Bluffs, NE-IA Metro Area & 2.91 & -0.14 \\ \hline
+    Orlando-Kissimmee-Sanford, FL Metro Area & 2.61 & -0.16 \\ \hline
+    Oshkosh-Neenah, WI Metro Area & 1.75 & -0.04 \\ \hline
+    Owensboro, KY Metro Area & 3.17 & 0.08 \\ \hline
+    Oxnard-Thousand Oaks-Ventura, CA Metro Area & 2.31 & -0.03 \\ \hline
+    Palm Bay-Melbourne-Titusville, FL Metro Area & 2.79 & -0.11 \\ \hline
+    Panama City, FL Metro Area & 2.78 & -0.16 \\ \hline
+    Parkersburg-Vienna, WV Metro Area & 0.0 & -0.31 \\ \hline
+    Pensacola-Ferry Pass-Brent, FL Metro Area & 2.07 & -0.18 \\ \hline
+    Peoria, IL Metro Area & 0.96 & -0.27 \\ \hline
+    Philadelphia-Camden-Wilmington, PA-NJ-DE-MD Metro Area & 6.69 & 0.08 \\ \hline
+    Phoenix-Mesa-Chandler, AZ Metro Area & 3.49 & -0.11 \\ \hline
+    Pine Bluff, AR Metro Area & 12.5 & 0.05 \\ \hline
+    Pittsburgh, PA Metro Area & 3.76 & 0.01 \\ \hline
+    Pittsfield, MA Metro Area & 2.0 & -0.16 \\ \hline
+    Pocatello, ID Metro Area & 2.53 & -0.07 \\ \hline
+    Port St. Lucie, FL Metro Area & 5.48 & 0.13 \\ \hline
+    Portland-South Portland, ME Metro Area & 3.07 & 0.09 \\ \hline
+    Portland-Vancouver-Hillsboro, OR-WA Metro Area & 11.36 & 0.41 \\ \hline
+    Poughkeepsie-Newburgh-Middletown, NY Metro Area & 1.92 & -0.03 \\ \hline
+    Prescott Valley-Prescott, AZ Metro Area & 0.0 & -0.2 \\ \hline
+    Providence-Warwick, RI-MA Metro Area & 2.82 & -0.05 \\ \hline
+    Provo-Orem, UT Metro Area & 0.0 & -0.06 \\ \hline
+    Pueblo, CO Metro Area & 2.26 & -0.37 \\ \hline
+    Punta Gorda, FL Metro Area & 0.0 & -0.14 \\ \hline
+    Racine, WI Metro Area & 5.63 & 0.08 \\ \hline
+    Raleigh-Cary, NC Metro Area & 1.9 & -0.02 \\ \hline
+    Rapid City, SD Metro Area & 6.78 & -0.01 \\ \hline
+    Reading, PA Metro Area & 0.0 & -0.17 \\ \hline
+    Redding, CA Metro Area & 8.33 & -0.01 \\ \hline
+    Reno, NV Metro Area & 2.27 & -0.21 \\ \hline
+    Richmond, VA Metro Area & 2.68 & -0.02 \\ \hline
+    Riverside-San Bernardino-Ontario, CA Metro Area & 6.62 & 0.06 \\ \hline
+    Roanoke, VA Metro Area & 0.32 & -0.15 \\ \hline
+    Rochester, MN Metro Area & 1.79 & -0.01 \\ \hline
+    Rochester, NY Metro Area & 3.5 & 0.01 \\ \hline
+    Rockford, IL Metro Area & 8.06 & -0.01 \\ \hline
+    Rocky Mount, NC Metro Area & 11.29 & 0.32 \\ \hline
+    Rome, GA Metro Area & 0.0 & -0.24 \\ \hline
+    Sacramento-Roseville-Folsom, CA Metro Area & 6.15 & 0.08 \\ \hline
+    Saginaw, MI Metro Area & 4.88 & -0.18 \\ \hline
+    Salem, OR Metro Area & 5.94 & 0.13 \\ \hline
+    Salinas, CA Metro Area & 5.71 & 0.08 \\ \hline
+    Salisbury, MD-DE Metro Area & 1.72 & -0.14 \\ \hline
+    Salt Lake City, UT Metro Area & 2.44 & -0.13 \\ \hline
+    San Angelo, TX Metro Area & 0.0 & -0.23 \\ \hline
+    San Antonio-New Braunfels, TX Metro Area & 3.83 & -0.16 \\ \hline
+    San Diego-Chula Vista-Carlsbad, CA Metro Area & 4.26 & -0.01 \\ \hline
+    San Francisco-Oakland-Berkeley, CA Metro Area & 7.31 & 0.07 \\ \hline
+    San Jose-Sunnyvale-Santa Clara, CA Metro Area & 4.73 & 0.03 \\ \hline
+    San Luis Obispo-Paso Robles, CA Metro Area & 5.51 & 0.14 \\ \hline
+    Santa Cruz-Watsonville, CA Metro Area & 3.07 & -0.12 \\ \hline
+    Santa Fe, NM Metro Area & 1.16 & -0.22 \\ \hline
+    Santa Maria-Santa Barbara, CA Metro Area & 1.85 & -0.14 \\ \hline
+    Santa Rosa-Petaluma, CA Metro Area & 3.03 & -0.12 \\ \hline
+    Savannah, GA Metro Area & 2.4 & -0.14 \\ \hline
+    Scranton--Wilkes-Barre, PA Metro Area & 1.59 & -0.2 \\ \hline
+    Seattle-Tacoma-Bellevue, WA Metro Area & 18.17 & 0.74 \\ \hline
+    Sebastian-Vero Beach, FL Metro Area & 1.89 & -0.05 \\ \hline
+    Sebring-Avon Park, FL Metro Area & 0.0 & -0.19 \\ \hline
+    Sheboygan, WI Metro Area & 6.67 & 0.24 \\ \hline
+    Sherman-Denison, TX Metro Area & 0.0 & -0.18 \\ \hline
+    Shreveport-Bossier City, LA Metro Area & 4.39 & -0.16 \\ \hline
+    Sierra Vista-Douglas, AZ Metro Area & 5.63 & 0.15 \\ \hline
+    Sioux City, IA-NE-SD Metro Area & 6.1 & 0.11 \\ \hline
+    Sioux Falls, SD Metro Area & 1.23 & -0.21 \\ \hline
+    South Bend-Mishawaka, IN-MI Metro Area & 2.48 & -0.18 \\ \hline
+    Spartanburg, SC Metro Area & 1.12 & -0.3 \\ \hline
+    Spokane-Spokane Valley, WA Metro Area & 4.67 & -0.02 \\ \hline
+    Springfield, IL Metro Area & 2.73 & -0.27 \\ \hline
+    Springfield, MA Metro Area & 6.03 & -0.01 \\ \hline
+    Springfield, MO Metro Area & 3.79 & -0.24 \\ \hline
+    Springfield, OH Metro Area & 0.0 & -0.18 \\ \hline
+    St. Cloud, MN Metro Area & 8.0 & 0.31 \\ \hline
+    St. George, UT Metro Area & 2.02 & -0.01 \\ \hline
+    St. Joseph, MO-KS Metro Area & 6.0 & 0.04 \\ \hline
+    St. Louis, MO-IL Metro Area & 3.91 & -0.11 \\ \hline
+    State College, PA Metro Area & 4.94 & 0.18 \\ \hline
+    Staunton, VA Metro Area & 1.39 & -0.05 \\ \hline
+    Stockton, CA Metro Area & 6.14 & -0.23 \\ \hline
+    Sumter, SC Metro Area & 9.26 & -0.0 \\ \hline
+    Syracuse, NY Metro Area & 4.15 & 0.03 \\ \hline
+    Tallahassee, FL Metro Area & 1.49 & -0.3 \\ \hline
+    Tampa-St. Petersburg-Clearwater, FL Metro Area & 4.15 & 0.02 \\ \hline
+    Terre Haute, IN Metro Area & 1.01 & -0.14 \\ \hline
+    Texarkana, TX-AR Metro Area & 6.67 & 0.04 \\ \hline
+    The Villages, FL Metro Area & 2.04 & -0.02 \\ \hline
+    Toledo, OH Metro Area & 2.98 & -0.17 \\ \hline
+    Topeka, KS Metro Area & 3.41 & -0.17 \\ \hline
+    Trenton-Princeton, NJ Metro Area & 5.36 & 0.05 \\ \hline
+    Tucson, AZ Metro Area & 1.94 & -0.21 \\ \hline
+    Tulsa, OK Metro Area & 4.04 & -0.16 \\ \hline
+    Tuscaloosa, AL Metro Area & 5.52 & 0.02 \\ \hline
+    Twin Falls, ID Metro Area & 3.45 & -0.02 \\ \hline
+    Tyler, TX Metro Area & 1.99 & -0.13 \\ \hline
+    Urban Honolulu, HI Metro Area & 5.91 & 0.13 \\ \hline
+    Utica-Rome, NY Metro Area & 1.06 & -0.14 \\ \hline
+    Valdosta, GA Metro Area & 6.76 & 0.15 \\ \hline
+    Vallejo, CA Metro Area & 8.82 & 0.15 \\ \hline
+    Victoria, TX Metro Area & 2.0 & -0.22 \\ \hline
+    Vineland-Bridgeton, NJ Metro Area & 4.35 & -0.06 \\ \hline
+    Virginia Beach-Norfolk-Newport News, VA-NC Metro Area & 5.67 & 0.06 \\ \hline
+    Visalia, CA Metro Area & 4.27 & -0.03 \\ \hline
+    Waco, TX Metro Area & 7.92 & 0.13 \\ \hline
+    Walla Walla, WA Metro Area & 2.47 & -0.03 \\ \hline
+    Warner Robins, GA Metro Area & 5.08 & -0.02 \\ \hline
+    Washington-Arlington-Alexandria, DC-VA-MD-WV Metro Area & 4.92 & 0.08 \\ \hline
+    Waterloo-Cedar Falls, IA Metro Area & 1.43 & -0.15 \\ \hline
+    Watertown-Fort Drum, NY Metro Area & 4.55 & 0.09 \\ \hline
+    Wausau-Weston, WI Metro Area & 4.11 & 0.07 \\ \hline
+    Weirton-Steubenville, WV-OH Metro Area & 5.45 & 0.19 \\ \hline
+    Wenatchee, WA Metro Area & 5.22 & 0.21 \\ \hline
+    Wheeling, WV-OH Metro Area & 1.61 & -0.13 \\ \hline
+    Wichita Falls, TX Metro Area & 3.85 & -0.03 \\ \hline
+    Wichita, KS Metro Area & 2.85 & -0.4 \\ \hline
+    Williamsport, PA Metro Area & 2.99 & 0.04 \\ \hline
+    Wilmington, NC Metro Area & 3.63 & -0.07 \\ \hline
+    Winchester, VA-WV Metro Area & 0.0 & -0.12 \\ \hline
+    Winston-Salem, NC Metro Area & 2.32 & -0.64 \\ \hline
+    Worcester, MA-CT Metro Area & 2.58 & -0.08 \\ \hline
+    Yakima, WA Metro Area & 5.38 & 0.1 \\ \hline
+    York-Hanover, PA Metro Area & 1.41 & -0.1 \\ \hline
+    Youngstown-Warren-Boardman, OH-PA Metro Area & 1.8 & -0.37 \\ \hline
+    Yuba City, CA Metro Area & 5.17 & 0.02 \\ \hline
+    Yuma, AZ Metro Area & 0.86 & -0.15 \\ \hline
+    \caption{Metropolitan Areas and their subreddits}
+	\label{table:app-a}
+\end{longtable}
+
 % Appendix A - Metro, subreddit

### 2022-06-26 analysis/get_comments.py
starting comment scraper

@@ -1,0 +1,72 @@
+import os
+import requests
+
+def get_users(crime_poster, non_crime_poster):
+    headers = {}
+    json_data = {
+        'query': {
+            'term': {
+                'data.subreddit': 'nyc',
+            },
+        },
+    }
+
+    while True:
+        try:
+            resp = requests.get(f"{os.environ['ES_ENDPOINT']}/reddit-posts/_search?pretty&size=10000",
+                auth=(os.environ['ES_USERNAME'], os.environ['ES_PASSWORD']), timeout=5, headers=headers, json=json_data)
+            if resp.status_code == 404:
+                continue
+        except requests.exceptions.ConnectionError as e:
+            continue
+        break
+
+    hits = resp.json()['hits']['hits']
+
+    for h in hits:
+        author = h['_source']['data']['author']
+        if h['_source']['about_crime'] == True:
+            if author in non_crime_poster:
+                non_crime_poster.remove(author)
+            crime_poster.add(author)
+        else:
+            if author not in crime_poster:
+                non_crime_poster.add(author)
+
+    print(len(non_crime_poster))
+    print(len(crime_poster))
+
+def get_comments(crime_poster, non_crime_poster):
+    url = "https://oauth.reddit.com/user/"
+
+    auth = requests.auth.HTTPBasicAuth(os.environ['REDDIT_CLIENT_ID'], os.environ['REDDIT_CLIENT_SECRET'])
+
+    data = {
+        'grant_type': 'password',
+        'username': os.environ['REDDIT_USER_NAME'],
+        'password': os.environ['REDDIT_PASSWORD'],
+    }
+
+    headers = {
+        'User-Agent': os.environ['REDDIT_USER_AGENT'],
+    }
+
+    res = requests.post('https://www.reddit.com/api/v1/access_token',
+                    auth=auth, data=data, headers=headers)
+
+    TOKEN = res.json()['access_token']
+
+    headers['Authorization'] = f"bearer {TOKEN}"
+    res = requests.get('https://oauth.reddit.com/api/v1/me', headers=headers)
+
+    print(res.json())
+
+
+def main():
+    crime_poster = set()
+    non_crime_poster = set()
+
+    get_users(crime_poster, non_crime_poster)
+    get_comments(crime_poster, non_crime_poster)
+
+main()

### 2022-06-26 analysis/get_comments.py
finished sentiment analysis

@@ -1,5 +1,6 @@
 import os
 import requests
+from textblob import TextBlob
 
 def get_users(crime_poster, non_crime_poster):
     headers = {}
@@ -37,8 +38,17 @@ def get_users(crime_poster, non_crime_poster):
     print(len(crime_poster))
 
 def get_comments(crime_poster, non_crime_poster):
-    url = "https://oauth.reddit.com/user/"
+    num_crime_posts = 0
+    sum_crime_posts = 0.0
+    crime_suspended = 0
+    crime_total = len(crime_poster)
 
+    num_safe_posts = 0
+    sum_safe_posts = 0.0
+    safe_suspended = 0
+    safe_total = len(non_crime_poster)
+
+    url = "https://oauth.reddit.com/user"
     auth = requests.auth.HTTPBasicAuth(os.environ['REDDIT_CLIENT_ID'], os.environ['REDDIT_CLIENT_SECRET'])
 
     data = {
@@ -57,10 +67,53 @@ def get_comments(crime_poster, non_crime_poster):
     TOKEN = res.json()['access_token']
 
     headers['Authorization'] = f"bearer {TOKEN}"
-    res = requests.get('https://oauth.reddit.com/api/v1/me', headers=headers)
+    #res = requests.get(f'{url}/walebluber/comments', headers=headers, params={'limit': 100})
 
-    print(res.json())
+    #print(res.json()['data']['children'][0]['data']['body'])
 
+    while len(crime_poster) > 0:
+        author = crime_poster.pop()
+        print(f'Author: {author}')
+
+        res = requests.get(f'{url}/{author}/comments', headers=headers, params={'limit':50})
+        if res.status_code == 404 or res.status_code == 403:
+            crime_suspended += 1
+            continue
+
+        children = res.json()['data']['children']
+
+        num_crime_posts += len(children)
+
+        for c in children:
+            statement = TextBlob(c['data']['body'])
+            sum_crime_posts += statement.sentiment.polarity
+
+    print(sum_crime_posts / num_crime_posts)
+    print(num_crime_posts)
+    print(crime_suspended)
+    print(crime_total)
+
+    while len(non_crime_poster) > 0:
+        author = non_crime_poster.pop()
+        print(f'Author: {author}')
+
+        res = requests.get(f'{url}/{author}/comments', headers=headers, params={'limit':50})
+        if res.status_code == 404 or res.status_code == 403:
+            safe_suspended += 1
+            continue
+
[…]

### 2022-06-26 paper/main.tex
added more to paper

@@
 
-\section{Sentiment Analysis}
-
-TODO
+\section{Sentiment Analysis and Overlap}
+
+\par From the data collected by our Reddit scraper, we have seen that crime discussion is widespread among the selected communities.
+However, while we have analyzed posts about crime, we have not yet analyzed the users that initiate this crime discussion.
+To do this, we have extracted all 1,197 unique posters from the 1,828 posts to \texttt{r/nyc}, the New York City subreddit.
+134 of these posters have posted about crime at least once, while 1,063 have not.
+Seven users have posted about crime five or more times.
+Additionally, of the 134 crime posters, five have had their account suspended since May 31st, 2022.
+This accounts for 3.7\% of the crime posters.
+Of the 1,063 non-crime posters, 27 have had their accounts suspended, or 2.5\%.
+After fetching the unique users, we gathered posts and comments from their user history.
+In total, 11,926 comments and posts were gathered from crime-posting users, while 87,658 comments and posts were gathered from non-crime-posting users.
+
+\par One method of measuring user interaction patterns is through performing sentiment analysis on post and comment data.
+In this case, we measure the mean polarity score of users who post about crime and compare it to the mean polarity score of users who don't post about crime.
+A lower polarity means that the input data is more negative, while higher scores mean that the sentiment is more positive (REF).
+This can indicate the potential nature of a poster; if their polarity score is low, then they are a consistently negative voice in the community.
+Enough negative voices can detract from a community and introduce conflict and disarray.
+
+\begin{table}[h!]
+    \centering
+    \small
+    \caption{Most active Metropolitan Areas per population}
+    %\begin{tabu} to 1.0\textwidth {| *{3}{c|} }
+    \begin{tabular}{| c | c | c |}
+    \hline
+     & Crime posters & Non-crime posters \\ \hline
+    Within \texttt{r/nyc} &  -0.07 & 0.09 \\ \hline
+    Outside of \texttt{r/nyc} & -0.07 & 0.10 \\ \hline
+	\end{tabular}
+	\label{table:table-6}
+\end{table}
+
+\par Table \ref{table:table-6} displays the results of the sentiment analysis on users that submitted a post to the New York City subreddit.
+Comments and posts were divided between those within \texttt{r/nyc} and those outside of the community.
+The sentiment of crime-posters was nearly identical within and outside of the community.
+These poster were more on the negative side, with neutrality laying at zero.
+Non-crime users were generally more positive, scoring 0.09 within the community and 0.10 outside of the community.
 

### 2022-06-26 analysis/count_dupes.py

@@ -1,0 +1,41 @@
+import os
+import requests
+from pprint import pprint
+
+def get_users(crime_poster):
+    headers = {}
+    json_data = {
+        'query': {
+            'term': {
+                'data.subreddit': 'nyc',
+            },
+        },
+    }
+
+    while True:
+        try:
+            resp = requests.get(f"{os.environ['ES_ENDPOINT']}/reddit-posts/_search?pretty&size=10000",
+                auth=(os.environ['ES_USERNAME'], os.environ['ES_PASSWORD']), timeout=5, headers=headers, json=json_data)
+            if resp.status_code == 404:
+                continue
+        except requests.exceptions.ConnectionError as e:
+            continue
+        break
+
+    hits = resp.json()['hits']['hits']
+
+    for h in hits:
+        author = h['_source']['data']['author']
+        if h['_source']['about_crime'] == True:
+            if author in crime_poster:
+                crime_poster[author] += 1
+            else:
+                crime_poster[author] = 1
+    pprint(crime_poster)
+
+def main():
+    crime_poster = {}
+
+    get_users(crime_poster)
+
+main()

### 2022-06-26 analysis/get_comments.py

@@ -71,6 +71,8 @@ def get_comments(crime_poster, non_crime_poster):
 
     #print(res.json()['data']['children'][0]['data']['body'])
 
+    '''SHOULD HAVE MADE THIS A FUNCTION LMAO'''
+
     while len(crime_poster) > 0:
         author = crime_poster.pop()
         print(f'Author: {author}')
@@ -82,11 +84,13 @@ def get_comments(crime_poster, non_crime_poster):
 
         children = res.json()['data']['children']
 
-        num_crime_posts += len(children)
+        #num_crime_posts += len(children)
 
         for c in children:
-            statement = TextBlob(c['data']['body'])
-            sum_crime_posts += statement.sentiment.polarity
+            if c['data']['subreddit'] == 'nyc':
+                statement = TextBlob(c['data']['body'])
+                sum_crime_posts += statement.sentiment.polarity
+                num_crime_posts += 1
 
     print(sum_crime_posts / num_crime_posts)
     print(num_crime_posts)
@@ -104,11 +108,13 @@ def get_comments(crime_poster, non_crime_poster):
 
         children = res.json()['data']['children']
 
-        num_safe_posts += len(children)
+        #num_safe_posts += len(children)
 
         for c in children:
-            statement = TextBlob(c['data']['body'])
-            sum_safe_posts += statement.sentiment.polarity
+            if c['data']['subreddit'] == 'nyc':
+                statement = TextBlob(c['data']['body'])
+                sum_safe_posts += statement.sentiment.polarity
+                num_safe_posts += 1
 
     print(sum_safe_posts / num_safe_posts)
     print(num_safe_posts)

### 2022-06-27 analysis/count_dupes.py
adding overlap data

@@ -25,7 +25,7 @@ def get_users(crime_poster):
     hits = resp.json()['hits']['hits']
 
     for h in hits:
-        author = h['_source']['data']['author']
+        author = h['_source']['data']['subreddit']
         if h['_source']['about_crime'] == True:
             if author in crime_poster:
                 crime_poster[author] += 1

### 2022-06-27 analysis/get_overlap.py

@@ -1,0 +1,104 @@
+import os
+import requests
+import csv
+
+def get_users(crime_poster, non_crime_poster):
+    headers = {}
+    json_data = {
+        'query': {
+            'term': {
+                'data.subreddit': 'nyc',
+            },
+        },
+    }
+
+    while True:
+        try:
+            resp = requests.get(f"{os.environ['ES_ENDPOINT']}/reddit-posts/_search?pretty&size=10000",
+                auth=(os.environ['ES_USERNAME'], os.environ['ES_PASSWORD']), timeout=5, headers=headers, json=json_data)
+            if resp.status_code == 404:
+                continue
+        except requests.exceptions.ConnectionError as e:
+            continue
+        break
+
+    hits = resp.json()['hits']['hits']
+
+    for h in hits:
+        author = h['_source']['data']['author']
+        if h['_source']['about_crime'] == True:
+            if author in non_crime_poster:
+                non_crime_poster.remove(author)
+            crime_poster.add(author)
+        else:
+            if author not in crime_poster:
+                non_crime_poster.add(author)
+
+    print(len(non_crime_poster))
+    print(len(crime_poster))
+
+def get_comments(poster_set):
+    subreddit_map = {}
+
+    url = "https://oauth.reddit.com/user"
+    sub_url = "https://oauth.reddit.com/r"
+    auth = requests.auth.HTTPBasicAuth(os.environ['REDDIT_CLIENT_ID'], os.environ['REDDIT_CLIENT_SECRET'])
+
+    data = {
+        'grant_type': 'password',
+        'username': os.environ['REDDIT_USER_NAME'],
+        'password': os.environ['REDDIT_PASSWORD'],
+    }
+
+    headers = {
+        'User-Agent': os.environ['REDDIT_USER_AGENT'],
+    }
+
+    res = requests.post('https://www.reddit.com/api/v1/access_token',
+                    auth=auth, data=data, headers=headers)
+
+    TOKEN = res.json()['access_token']
+
+    headers['Authorization'] = f"bearer {TOKEN}"
+
+    while len(poster_set) > 0:
+        author = poster_set.pop()
+        print(f'Author: {author}')
+
+        res = requests.get(f'{url}/{author}/comments', headers=headers, params={'limit':50})
+        if res.status_code == 404 or res.status_code == 403:
+            continue
+
+        children = res.json()['data']['children']
+
+        #num_crime_posts += len(children)
+
[…]

### 2022-06-28 paper/main.tex
fixing plots

@@
 \usepackage[sorting=none]{biblatex}
-%\addbibresource{References.bib}
+\addbibresource{References.bib}
 
@@
 \chapter*{Abstract}
-\par The abstract is mandatory.
-\par The maximum acceptable length for an abstract to be published in Dissertation Abstracts International (DAI) is 350 words.
-The maximum acceptable length for an abstract to be published in Master’s Thesis Directories (MTD) is 150 words.
-However, an abstract within the dissertation or thesis need not be limited.
-The student may prepare a lengthy abstract for inclusion in the thesis or dissertation and a more concise summary for publication in DAI/MTD.
-\par The abstract is expected to give a succinct account of the student's work so that a reader can quickly learn the essential contents and results.
-A typical abstract includes a statement of the problem, an account of procedure or methods followed, and an account of main results and conclusions.
-\par Abstracts must be prepared carefully, since they are published in DAI/MTD without editing or revision.
+\par The relationship between crime and the media is an oft studied subject.
+Researchers have long analyzed how the ubiquity of crime reporting in traditional media can affect how people view public safety in their communities and how factors such as population size, reported crime rates, and political affiliation can impact this trend.
+However, in the age of the Internet, social media has become increasingly relevant when compared to traditional media.
+Despite this, the level of research on crime and social media has not rivaled social media's meteoric rise.
+\par In this paper, we analyze the submission of crime-related posts to communities representing the 384 Metropolitan Areas of the United States on the social media website Reddit.
+We found that crime discussion is more common in larger communities and communities that lean more liberal politically, while reported crime rates do not have a strong impact.
 
@@
 \newpage
-\begin{doublespace}
-\chapter*{Preface}
-\par The preface is optional. If necessary, the following information should be included:
-\par For previously published works, cite each published piece fully and indicate whether your studies or articles are being republished in their entirety and in the original wording, or whether they have been revised for the dissertation.
-Indicate that your studies or articles are being included because they were part of the programmatic line of research that comprised the dissertation and that including them provides a coherent and appropriately sequenced investigation.
-Describe your (the dissertation author) role in the published work.
-Certify that permission to republish these works in the dissertation has been obtained from the publisher or owner.
-\par For images, identify the ones for which permission has been received by figure number and with reference to the copyright holder (whether an individual or institution) and certify that permission has been obtained.
-You may wish to add that all other images are in the public domain or being used under a public license or fair use.
-\end{doublespace}
-\newpage
 
@@
 \chapter*{List of Abbreviations}
-Include any listing of abbreviations on this page.
-%\printnomenclature
+
+\begin{doublespace}
+
+API  Application Programming Interface
+
+FBI  Federal Bureau of Investigation
+
+MSA  Metropolitan Statistical Area
+
+REST Representational State Transfer
+
+UA  Urbanized Area
+
+UC  Urbanized Cluster
+
+UCR  Uniform Crime Reporting
+
+US  United States
+
+\end{doublespace}
 
@@
 \chapter{Introduction}
-\par The following text is only included to take up space and provide a visual sense of the layout of your paper.
-It is written in Latin for no reason other than to encourage you to bypass it as not being necessary information for you to spend your time reading.
-\par Sed ut perspiciatis unde omnis iste natus error sit voluptatem accusantium doloremque laudantium, totam rem aperiam, eaque ipsa quae ab illo inventore veritatis et quasi architecto beatae vitae dicta sunt explicabo.
-Nemo enim ipsam voluptatem quia voluptas sit aspernatur aut odit aut fugit, sed quia consequuntur magni dolores eos qui ratione voluptatem sequi nesciunt.
-Neque porro quisquam est, qui dolorem ipsum quia dolor sit amet, consectetur, adipisci velit, sed quia non numquam eius modi tempora incidunt ut labore et dolore magnam aliquam quaerat voluptatem.
-Ut enim ad minima veniam, quis nostrum exercitationem ullam corporis suscipit laboriosam, nisi ut aliquid ex ea commodi consequatur?
-Quis autem vel eum iure reprehenderit qui in ea voluptate velit esse quam nihil molestiae consequatur, vel illum qui dolorem eum fugiat quo voluptas nulla pariatur?
+
+\section{Motivation}
+
+\par lol
+
+\section{Outline}
+
+\par yee
 
 \chapter{Background and Related Work}
-\par Each chapter should begin at the top of a new page, with a two-inch top margin.\footnote{This is your first footnote, if your chosen style manual calls for footnotes rather than endnotes. \\} 
-\par Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.\footnote{This is your second footnote.
-There should be a space, as shown, between each note (whether footnote or endnote).}
-
-\section{Media, Politics, and Perception of Crime}
+
+\section{Traditional Media}
 \par TODO: papers about historical media and crime, modern issues, social media effects
+
+\section{Social Media}
+\par TODO: what reddit is and its role in misinformation. crime and social media papers
+
+\par Reddit citation test \cite{ftahmsabi}
 
@@
 
-\section{Reddit as Social Media}
-\par TODO: what reddit is and its role in misinformation
-
-\begin{figure}[ht]
-    \centering
-    \begin{minipage}[t]{0.8\textwidth}
-    \textit{Follow this list to ensure your pages are in the correct order. \\}
-	\begin{enumerate}
-	    \item Title page (mandatory)
-	    \item Copyright notice (mandatory)
-	    \item Committee page (mandatory)
-	    \item Abstract (mandatory)
-	    \item Dedication (optional)
-	    \item Acknowledgments (optional)
-	    \item Preface (optional)
-	    \item Table of contents (mandatory)
-	    \item List of tables (include list if manuscript includes tables)
-	    \item List of figures (include list if manuscript includes figures)
-	    \item List of plates (include list if manuscript includes plates)
-	    \item List of abbreviations (include if needed)
-	    \item Body of manuscript (mandatory)
-	    \item Appendix(es) (if necessary)
-	    \item Notes (include if necessary)
-	    \item Bibliography (mandatory)
-	\end{enumerate}
-	\end{minipage}
-    \caption{Sequence of pages for thesis or dissertation.}
-	\label{fig:fig-1}
-\end{figure}
-
 \chapter{Analysis}
@@
 \section{Data Overview}
-\par The subreddit-level analysis requires a variety of different data inputs.
-These data inputs can be divided into two major subcategories: post and comment data from Reddit itself and data that provide contextual or qualitative information.
 
 \subsection{Reddit Data}
-\par The Reddit dataset contains posts from the subreddits of the 384 MSAs of the United States as of March 2020 (REF).
-Appendix (REF) provides a full list of subreddits used.
+\par The Reddit dataset contains posts from the subreddits of the 384 MSAs of the United States as of March 2020 \cite{censusmetro}.
 From this list of subreddits, we scrape and store all posts that users submit.
@@
 \begin{figure}[ht]
-    \includegraphics[width=\textwidth]{Images/timeline.png}
+    \includegraphics[width=0.75\textwidth]{Images/timeline.pdf}
     \caption{Number of daily posts across all subreddits}
@@
 To do this, a regular expression checks if a post's title or a post's link's URL contains a crime-related keyword.
-Appendix (REF) lists the keywords used.
 These keywords were derived from actions that constitute violent crime and their synonyms, as well as generic crime-related words.
+In total, 46 keywords and their derivatives are used.
 If the regular expression returns a hit, a flag is raised in the database denoting that the post is about crime.
-Overall, 6,792 posts are estimated to discuss crime.
-
-TODO: User Scraper stuff
+Overall, 6,792 of the collected posts are estimated to discuss crime.
+
+\par Due to the nature of text analysis, a number of false positives might be considered, while some false negatives go undetected.
+False negatives can be hard to detect, as they include dog-whistles, local-dependent terms, and ambiguous references (REF).
+Certain posters may choose to keep their posts ambiguous so as to keep their intentions visible to only a small group (REF).
+
+\par To determine the rate of false positives, we analyze a sample of scraped posts.
+We look for phrases such as ``I shot a picture'' that do not relate to crime, but contain a crime-related keyword.
+Of a sample of 400 posts, we find that 36 posts do not relate to crime, for an accuracy rate of 91\%.
+Similar analysis done on the social media site reached a rate of 66\% \cite{curiel}.
 
@@
 The large population contains 56 members, the medium bin contains 54 members, the small bin contains 113 members, and the very small bin contains 161 members.
-Appendix (REF) contains the populations of all MSAs.
 
@@
 The Very Conservative bin contains 112 members, the Conservative bin contains 103 members, the Moderate bin contains 57 members, the Liberal bin contains 73 members, and the Very Liberal bin contains 39 members.
-Appendix (REF) contains the voting patterns of all MSAs.
 
@@
 This data is derived from the FBI's Uniform Crime Reporting statistics (REF) \footnote{Data from the FBI mostly comes from the year that is most recent, 2019.
-However, not all municipalities report information, so there are slight estimations in the data (REF).
-Additionally, not all MSAs have documented 2019 data, so 2018 or 2017 data are used instead.
-The year gathered is documented in Appendix (REF)}.
+However, not all municipalities report information, so there are slight estimations in the data (REF).}.
 These values range from a minimum of 44.3/100,000 (Bangor, ME) to a maximum of 1,397.2/100,000 (Birmingham-Hoover, AL).
 Documented crime data is also normalized using min-max normalization so that it can be compared to a similarly normalized crime discussion value from the Reddit data.
-Appendix (REF) contains the documented crime rate of all MSAs.
 
@@
 
-\par To gather the data, the scraper first sends requests to the Reddit REST API (REF).
+\par To gather the data, the scraper first sends requests to the Reddit REST API \cite{reddit}.
 We use the \texttt{new} endpoint for each subreddit to check the most recent posts.
@@
 If something unexpected occurs and the tool goes down, it will simply be restarted by Kubernetes.
-Figure (REF) details the entire data scraping process.
-
-(FIG)
-
-\section{Raw Results}
+
+\section{Results}
 
@@
     \centering
-    \includegraphics[width=0.75\textwidth]{Images/bar-population.png}
+    \includegraphics[width=0.75\textwidth]{Images/bar-population.pdf}
     \caption{Comparison of discussed crime and documented crime by population}
@@
     \centering
-    \includegraphics[width=0.75\textwidth]{Images/cdf.png}
+    \includegraphics[width=0.75\textwidth]{Images/cdf.pdf}
     \caption{Crime discussion by MSA population class}
@@
     \centering
-    \includegraphics[width=0.75\textwidth]{Images/bar-politics.png}
+    \includegraphics[width=0.75\textwidth]{Images/bar-politics.pdf}
     \caption{Comparison of discussed crime and documented crime by political class}
@@
 
-\begin{figure}[!tbp]
-  \centering
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{Images/scatter-politics-mid-large.png}
-    \caption{Perceived crime by political leaning}
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.75\textwidth]{Images/scatter-politics-mid-large.pdf}
+    \caption{Crime discussion by percent voting Democrat}
     \label{fig:scatter-1}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{Images/scatter-crime-mid-large.png}
-    \caption{Documented crime by political leaning}
-    \label{fig:scatter-2}
-  \end{minipage}
 \end{figure}
@@
 MSAs that lean conservative, such as Birmingham-Hoover, AL and Kansas City, MO-KS have among the highest crime rates, as well as more politically moderate cities, such as Memphis, TN-MS-AR.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.75\textwidth]{Images/scatter-crime-mid-large.pdf}
+    \caption{Crime discussion by documented crime rate}
+    \label{fig:scatter-2}
+\end{figure}
 
@@
     \centering
-    \caption{General formatting requirements for thesis or dissertation}
+    \caption{MSAs by highest and lowest difference score}
     %\begin{tabu} to 1.0\textwidth {| *{3}{c|} }
@@
 
-\section{Sentiment Analysis and Overlap}
+\section{Sentiment Analysis}
 
@@
     \small
-    \caption{Most active Metropolitan Areas per population}
+    \caption{Sentiment polarity scores for \texttt{nyc} users}
     %\begin{tabu} to 1.0\textwidth {| *{3}{c|} }
@@
 These poster were more on the negative side, with neutrality laying at zero.
-Non-crime users were generally more positive, scoring 0.09 within the community and 0.10 outside of the community.
+Non-crime posting users were generally more positive, scoring 0.09 within the community and 0.10 outside of the community.
 
@@
 \par We have discussed the nature and prevalence of crime discussion on Reddit, a social media website, as it pertains to location-based communities.
-To obtain the necessary data and information, we have created a highly available Reddit scraper that fetches all posts from communities that represent the 384 Metropolitan Statistical Areas of the United States.
+To obtain the necessary data and information, we have created a highly resilient Reddit scraper that fetches all posts from communities that represent the 384 Metropolitan Statistical Areas of the United States.
 The scraper gathered 161,166 posts over a two-month time span.
@@
 \newpage
-\addcontentsline{toc}{chapter}{Bibliography/ References/ Works Cited}
-\chapter*{Bibliography/ References/ Works Cited}
+\addcontentsline{toc}{chapter}{References}
 \setstretch{1.0}
 \fontsize{10}{10pt} \selectfont
-References should be single-spaced. The style and format for references should follow the style guide used for the rest of the dissertation. \newline \newline
-Put an extra space in between entries.
 
 % Remove lines 284, 287-288 and uncomment lines 291-292 while using template
-%\renewcommand{\bibname}{Bibliography/References/Works Cited}
-%\printbibliography
+\renewcommand{\bibname}{References}
+
+\printbibliography
 

### 2022-06-29 paper/main.tex
added intro

@@
 
-\section{Motivation}
-
-\par lol
-
-\section{Outline}
-
-\par yee
+\par Crime has long shaped people's lives.
+The fear of crime has inspired historical events (REF), shaped elections (REF), and motivated social movements (REF).
+While fear of crime has occurred organically throughout history, some people or groups have elevated crime cases for political or monetary gain (REF).
+The media is one such group that potentially seeks to gain from crime discussion.
+The relationship between the media and perceptions of crime has been the subject of many studies in fields such as sociology and criminology (REF).
+Through mediums such as television (REF) and print (REF), researchers have long analyzed how the prevalence of crime reporting might affect consumer's perceptions of public safety.
+
+\par While traditional media such as television and newspapers are frequently the subject of research, they have become increasingly less relevant.
+As traditional media declines, social media, such as Twitter, Facebook, and Reddit, has risen in its place.
+As a result, an increasing number of people consume news through social media (REF), which includes topics such as crime.
+However, social media is not without its flaws.
+Due to the free and open nature of who can post on social media, submissions containing misinformation (REF) and manipulation of content (REF) have remained a challenge for social media companies to reign in.
+
+\par As social media begins to fill traditional media's niche, one might wonder how the landscape of crime reporting and discussion might change.
+In this work, we analyze the discussion of crime on the social media website Reddit.
+Specifically, we examine how crime discussion takes shape on the 384 communities, known as subreddits, that represent the Metropolitan Statistical Areas of the United States.
+To measure crime discussion, we have developed a Reddit scraper to fetch all of the posts from the 384 communities.
+We have also developed techniques to identify posts that discuss crime while minimizing false positives.
+We analyze the data collected by the scraper to determine a community's level of crime discussion in comparison to its population, voting patterns, and documented crime rate.
+Lastly, we dive into the posting histories of users who post to Reddit's New York City community to identify any further trends or patterns.
 
@@
 \section{Social Media}
+
+\subsection{Reddit}
+
 \par TODO: what reddit is and its role in misinformation. crime and social media papers
@@
 
-\section{Sentiment Analysis}
+\section{Sentiment Analysis and Overlap}
 
@@
 However, while we have analyzed posts about crime, we have not yet analyzed the users that initiate this crime discussion.
-To do this, we have extracted all 1,197 unique posters from the 1,828 posts to \texttt{r/nyc}, the New York City subreddit.
+In doing so, we can potentially identify trends in the data that could highlight motivations behind crime posters or their submission patterns.
+We can also attempt to identify if crime posters are truly local by seeing if they overlap with other state and local subreddits.
+
+\par To analyze users' posting histories, we extract their submission and comment data.
+For this work, we use posters to \texttt{r/nyc}, the New York City subreddit as a sample.
+We have extracted all 1,197 unique posters from the 1,828 posts to \texttt{r/nyc}.
 134 of these posters have posted about crime at least once, while 1,063 have not.
@@
 
+\par Another method of analyzing user interaction patterns is through identifying other communities that \texttt{r/nyc} members post in.
+This can potentially identify important posting trends.
+Examples include location identity and political affiliation.
+To measure this, we use the Jaccard Index.
+The Jaccard index can be defined as:
+
+(REF)
+
+\par Table \ref{table:table-7} displays the subreddits with the highest overlap for both crime and non-crime posters.
+Crime posters and non-crime posters alike share some common, New York City-related subreddits, such as \texttt{NYCBike}.
+However, crime posters have high overlap between two subreddits specifically meant to discuss crime in New York City: \texttt{CrimeInNYC} and \texttt{NYStateOfMind}.
+
+\begin{table}[h!]
+    \centering
+    \small
+    \caption{Subreddits with highest overlap by poster type}
+    %\begin{tabu} to 1.0\textwidth {| *{3}{c|} }
+    \begin{tabular}{| c | c | c | c |}
+    \hline
+    \multicolumn{2}{|c|}{Crime poster} & \multicolumn{2}{|c|}{Non-crime poster} \\ \hline
+    Subreddit & Score & Subreddit & Score\\ \hline
+    \texttt{CrimeInNYC} & 0.83 & \texttt{nycrail} & 0.81 \\ \hline
+    \texttt{Judaism} & 0.42 & \texttt{AskNYC} & 0.64 \\ \hline
+    \texttt{AskNYC} & 0.29 & \texttt{RunNYC} & 0.48 \\ \hline
+    \texttt{NYCbike} & 0.25 & \texttt{astoria} & 0.42 \\ \hline
+    \texttt{newyorkcity} & 0.21 & \texttt{Brooklyn} & 0.43 \\ \hline
+    \texttt{NYYankees} & 0.16 & \texttt{NYCBike} & 0.42 \\ \hline
+    \texttt{rangers} & 0.15 & \texttt{newyorkcity} & 0.40 \\ \hline
+    \texttt{RealTesla} & 0.14 & \texttt{jerseycity} & 0.37 \\ \hline
+    \texttt{NYStateOfMind} & 0.12 & \texttt{BostonU} & 0.33 \\ \hline
+    \texttt{GenX} & 0.11 & \texttt{Baruch} & 0.32 \\ \hline
+	\end{tabular}
+	\label{table:table-7}
+\end{table}
+
+\par From the overlap data, we can see that crime is a frequent topic of discussion even outside the \texttt{nyc} subreddit for the identified crime posters.
+However, the overlap with several New York City-related communities indicates that many of the crime posters have some relation to the city itself.
+
+\par While the two types of posters share some subreddits, their political community overlap is fairly different.
+To identify political subreddits, we derive the methodology from (REF).
+Table \ref{table:table-8} shows the political subreddits with the largest amount of overlap.
+
+\begin{table}[h!]
+    \centering
+    \small
+    \caption{Political subreddits with highest overlap by poster type}
+    %\begin{tabu} to 1.0\textwidth {| *{3}{c|} }
+    \begin{tabular}{| c | c | c | c |}
+    \hline
+    \multicolumn{2}{|c|}{Crime poster} & \multicolumn{2}{|c|}{Non-crime poster} \\ \hline
+    Subreddit & Score & Subreddit & Score\\ \hline
+    \texttt{neoliberal} & 0.05 & \texttt{VoteDEM} & 0.16 \\ \hline
+    \texttt{LockdownSkepticism} & 0.03 & \texttt{tuesday} & 0.10 \\ \hline
+    \texttt{Conservative} & 0.02 & \texttt{neoliberal} & 0.05 \\ \hline
+	\end{tabular}
+	\label{table:table-8}
+\end{table}
+
+\par Here, we see that the two groups diverge on political opinions.
+Those that post about crime trend more towards the right; \texttt{LockdownSkepticism} is a community critical of Covid-19 restrictions and \texttt{Conservative} is Reddit's largest right-leaning political community.
+Non-crime posters are active in politically moderate communities such as \texttt{tuesday} and \texttt{neoliberal}, as well as \texttt{VoteDem}, which supports the Democratic Party.
+
+\par From our user-level analysis, we have identified several characteristics of crime posters.
+First, these users are consistently more negative than non-crime posting users.
+They post about crime frequently, as indicated by their significant overlap with crime discussion specific communities.
+However, they are often local to the communities in which they post, as they have significant overlap to location specific hobby and sport communities.
+Lastly, those that post about crime are more active in conservative political communities than those who don't post about crime.
+
 \chapter{Conclusion}
@@
 \par While this paper provides a first look at the crime discussion dynamics on Reddit, there are several paths that continued research could explore.
-One pathway of future work on the relationship between crime discussion and social media can include a more in-depth analysis of users that post about crime.
-By delving deep into these users' posting histories, we can attempt to determine if there is any sort of coordinated effort to push crime discussion in certain communities.
+One pathway of future work on the relationship between crime discussion and social media could include a more in-depth analysis of users that post about crime beyond the sample that we took.
 Another approach could be applying the tool and analysis used on Reddit to other social media platforms, such as Facebook or Nextdoor, to determine if this phenomenon is Reddit-specific.

### 2022-06-30 paper/main.tex
started bnrw

@@
 \par The relationship between crime and the media is an oft studied subject.
-Researchers have long analyzed how the ubiquity of crime reporting in traditional media can affect how people view public safety in their communities and how factors such as population size, reported crime rates, and political affiliation can impact this trend.
+Researchers have long analyzed how the ubiquity of crime reporting in traditional media can affect people's view of public safety in their communities and how various factors can impact this trend.
 However, in the age of the Internet, social media has become increasingly relevant when compared to traditional media.
-Despite this, the level of research on crime and social media has not rivaled social media's meteoric rise.
+Despite this, the level of research on crime and social media has not rivaled social media's rise.
 \par In this paper, we analyze the submission of crime-related posts to communities representing the 384 Metropolitan Areas of the United States on the social media website Reddit.
-We found that crime discussion is more common in larger communities and communities that lean more liberal politically, while reported crime rates do not have a strong impact.
+We find that crime discussion is more common in larger communities and communities that lean more liberal politically.
+Reported crime rates do not have a strong impact.
 
@@
 
+\section{Geography}
+
+\subsection{Scale}
+
+\par Before we begin the gathering of the data, we must first understand the scale at which the data should be collected.
+First, we are collecting data that pertains to the United States.
+Second, in a general sense, we want to measure at a city-level scale.
+The city is the base-level at which a critical mass of population can support an online community; a city provides a geographic center and a name to associate with a community.
+However, the definition of a city is rather murky.
+The definition varies on a state-by-state basis due to the nature in which a state delineates county-level subdivisions.
+All states are broken down into counties, but differ in how counties are partitioned.
+For example, New York breaks down counties into towns, cities, and villages (REF), while North Dakota only subdivides counties into cities, with excluded areas remaining unincorporated (REF).
+In this way, we can think of city limits and city populations as somewhat arbitrary.
+There is no consistent, uniform definition, so cities should not be compared to each other.
+To equalize these differences, we use statistical area definitions provided by the United States Census Bureau.
+
+\subsection{Census Defined Statistical Areas}
+
+\par The Census Bureau provides several statistical area definitions to normalize city population and sizes.
+The first and most accurate definition is for Urban Areas (UAs) and Urban Clusters (UCs).
+UAs are dense clusters of people that house over 50,000 people.
+UCs are similarly measured dense clusters of people with between 2,500 and 50,000 people.
+UAs and UCs are computed by first identifying a dense cluster of census blocks, the smallest census geography (REF).
+From here, the UA or UC snakes off from the central core to include housing that fits the density requirements in less dense census blocks (REF).
+This process creates the ``true'' city limits, which are unaffected by municipal boundaries.
+
+\par While Urban Areas are an effective method of measuring the true sizes of cities, they are difficult to map and obtain statistics on.
+Their shapes are generally compact and do not have any sort of uniform, governing body.
+To alleviate these issues, we choose Metropolitan Statistical Areas (MSAs) as our scale.
+MSAs consist of the county or counties in which an Urban Area lies, alongside any counties in which 25\% of the population commutes to a core county (REF).
+In this way, we gain the population measurement accuracy of UAs with the ease of data access from state-defined municipalities.
+MSAs also lump together similar, nearby cities, such as New York, Newark, and Jersey City, to avoid redundant analysis.
+As of March 2020, there are 384 Metropolitan Statistical Areas, each with a corresponding Reddit community (REF).
+
 \section{Traditional Media}
@@
 \par Reddit citation test \cite{ftahmsabi}
-
-\section{Geography}
-\par TODO: explanation of geographical terms (urban areas, MSAs, etc)
 

### 2022-07-01 paper/main.tex
more on bnrw

@@
 MSAs also lump together similar, nearby cities, such as New York, Newark, and Jersey City, to avoid redundant analysis.
-As of March 2020, there are 384 Metropolitan Statistical Areas, each with a corresponding Reddit community (REF).
+As of March 2020, there are 384 Metropolitan Statistical Areas (REF), each with a corresponding Reddit community.
 
 \section{Traditional Media}
-\par TODO: papers about historical media and crime, modern issues, social media effects
+
+% REFS:
+% https://books.google.com/books?id=BmwuDwAAQBAJ&lpg=PP1&ots=_PlVBghHER&dq=media%20and%20crime&lr&pg=PP1#v=onepage&q=media%20and%20crime&f=false
+% https://doi.org/10.1177/0002716295539001011
+% https://doi.org/10.1177/0002764296039004003
+% https://doi.org/10.1177/19401612211020929
+% https://www.cambridge.org/core/books/television-and-its-viewers/83C017F8F8416B5D5F2716EBE5D354BF
+% http://personal.psu.edu/exs44/597b-Comm&Crime/Wilson-Kelling-Broken%20Windows.pdf
+% https://researchgate.net/profile/Tracey-Meares-2/publication/268224149_The_Law_and_Social_Science_of_Stop_and_Frisk/links/54665ea60cf25b85d17f6112/The-Law-and-Social-Science-of-Stop-and-Frisk.pdf
+% https://oxford.universitypressscholarship.com/view/10.1093/acprof:oso/9780195369083.001.0001/acprof-9780195369083
+
+\par Traditional media, such as television, newspapers, magazines, and radio, have long been intertwined with a fascination for crime.
+Live manhunts for people such as OJ Simpson (REF 1) and the Boston Bombers (REF ?) have captured and enthralled viewers and readers.
+However, while high-profile cases garner much of the attention, local and lower-profile cases often inhabit newspaper columns and television segments.
+It is with these cases that people grow uneasy with the sense of public safety in their community.
+A flurry of reporting on violent acts can increase worry, stress, and fear that crime is rising, even if the documented crime statistics show that crime has not increased (REF 3).
+
+\par An increase in a fear of crime can have implications beyond elevated negative emotions.
+Fear of crime has far-reaching political social (REF 1), (REF ?), and institutional (REF 2) impacts.
+Belief in excessive amounts of crime can lead to loss of community cohesion (REF 3).
+(REF 3) found that as television news media consumption increased, distrust both in the local community and the world ``out there'' increased.
+Additionally, media creators often sensationalized stories, turning unfortunate incidents into grim spectacles.
+Those that perceived crime to be worse than others were more likely to perform excessive crime prevention actions, such as not leaving their house or engaging with the neighborhood.
+
+\par (REF 4) describes how the prevalence of crime discussion affected the 2016 presidential election in the United States.
+The authors found that voters who consumed more television in turn consumed more campaign advertisements, of which many were about issues such as crime and violence.
+Frequent crime media consumers predict crime and violence issues to be worse than they really are (REF 5).
+Furthermore, the authors found that excessive crime reporting and media exposure had impacts on voting patterns; those that believed crime to be worse tended to vote for more conservative candidates.
+
+\par Worry of crime victimization can lead to the creation of institutional policies meant to combat the perceived threat.
+One notable example is the idea of Broken Windows Theory (REF 6) and a practice that stemmed from its development, known as stop and frisk (REF 7).
+Broken Windows Theory states that visible signs of crime and disorder lead to further crimes and disorder (REF 6).
+Essentially, the theory states that ignoring minor criminal incidents can lead to more frequent and serious issues.
+Acting on this theory, the New York Police Department instituted a stop and frisk policy, in which police officers temporarily detained civilians suspected of carrying illegal objects (REF 7).
+The effectiveness of the policy, while believed to be effective at the time, has since come under scrutiny.
+Researchers found that only 6\% of stops resulted in arrests (REF 7) and that there is no clear proof that stop and frisk contributed to the decline in crime in New York City (REF 8).
+Stop and frisk was removed as a policy in 2013 when it was deemed unconstitutional (REF 7).
 
 \section{Social Media}
+
+\subsection{Social Media and Crime}
 
@@
 \begin{figure}[ht]
+    \centering
     \includegraphics[width=0.75\textwidth]{Images/timeline.pdf}

### 2022-07-02 paper/main.tex
more bnrw

@@
 
+\subsection{Geography and the Internet}
+
+% TODO
+
 \section{Traditional Media}
@@
 % https://oxford.universitypressscholarship.com/view/10.1093/acprof:oso/9780195369083.001.0001/acprof-9780195369083
+% https://policycommons.net/artifacts/1817184/news-consumption-across-social-media-in-2021/2554124/
+% https://papers.ssrn.com/sol3/papers.cfm?abstract_id=2771080
 
@@
 
+\par While the relationship between traditional media and crime has been thoroughly researched, the relationship between social media and crime has not been as rigorously explored.
+Social media, which originally started as a method of connecting with friends and family, has grown and evolved beyond its humble beginnings.
+Social media sites, such as Twitter, are now significant sources of new for many Americans (REF - LR: What is twitter?).
+(REF 9) found that nearly half of Americans consume their news from social media sites like Twitter, Facebook, and Reddit.
+This trend coincides with the decline of traditional media.
+Printed media, such as newspapers and magazines, as well as televised media, has consistently declined since the explosive growth of the Internet (REF 10).
+Despite this, research on social media remains sparse.
+
+% Paragraph about relevant paper
+
+(REF) detail the ecosystem of crime discussion on Twitter.
+Specifically, they look at how often crime discussion appears in Tweets posted from users in Latin American countries.
+Using Twitter's geolocation tags, Tweets are subdivided down to the municipality that the original user posted from.
+From here, the authors compared Twitter crime discussion rates to city-level documented crime rates.
+They did not find a correlation between high frequencies of crime-related Tweets and high rates of reported crime.
+The authors conclude that the Tweets do not accurately represent actual rates of crime, but they effectively capture the worry of crime in a community.
+
+% Paragraph about misinformation
+
+(REF) introduce an interesting observation: some of the crime-related Tweets are highly sensationalized or completely untrue.
+In this way, social media differs from traditional media.
+Traditional media acts as a gatekeeper (REF 2), where only select stories and viewpoints emerge and some degree of factchecking generally exists (REF ?).
+Social media, on the other hand, allows for a more diverse set of viewpoints and opinions.
+However, as there is generally a limited amount of moderation (REF ?) on social media platforms, blatantly false stories can spread across sites (REF).
+This proliferation of misinformation has become increasingly impactful in the United States.
+It has affected important events in recent American history, including presidential elections (REF ?) and the the response to the Covid-19 pandemic (REF ?).
+Despite attempts to curb the spread of misinformation on social media (REF ?), falsehoods and panics continue to spread across the web.
+
 \subsection{Reddit}
 
-\par TODO: what reddit is and its role in misinformation. crime and social media papers
-
-\par Reddit citation test \cite{ftahmsabi}
+% R1: https://arxiv.org/pdf/2010.10397.pdf
+% R2: https://wapo.st/2Xvbvae
+% R3: https://arxiv.org/abs/1804.07354
+% R4: https://dl.acm.org/doi/abs/10.1145/3134666
+% R5: https://ojs.aaai.org/index.php/ICWSM/article/view/18053
+% R6: https://datacompass.lshtm.ac.uk/id/eprint/2982/
+% R7: https://social.techjunkie.com/demographics-reddit (REDDIT DEMOGRAPHICS)
+% R8: https://dl.acm.org/doi/pdf/10.1145/3512901
+% R9: http://fsnagle.org/papers/potts2013reddit.pdf
+
+\par While Facebook (REF ?) and Twitter (REF ?) face much of the backlash from outrage directed towards online misinformation, smaller websites, like Reddit, play a role in the distribution of sensationalized stories and misinformation as well.
+Reddit communities, also known as subreddits, allow users to post self-made content or link content from other parts of the web.
+Subreddits are dedicated to a certain topic, such as fishing, political groups, or real-life communities.
+Subreddits can be created by anyone and are run by volunteer moderators.
+As moderators are a varied group of individuals, they represent a diverse set of viewpoints not beholden to any set of limits.
+In this way, misinformation can seep into communities, as there are differing levels of moderation among subreddits.
+To combat rouge communities and moderators, Reddit has moved to ban certain subreddits that consistently break rules (REF R1).
+
+\par Several Reddit communities have been the subject of studies on misinformation.
+One such subreddit is known as \texttt{The\_Donald} (TD).
+TD, which acted as the support community for former President Donald Trump, spread unsubstantiated conspiracy theories, such as Pizzagate (REF R2) and engaged in harassment of other communities on the website (REF - extracting inter...).
+TD was eventually quarantined and banned from the site, leading users to create their own Reddit offshoot website (REF R1).
+However, TD spread misinformation with little intervention for the nearly five years that it survived on the site (REF R1).
+This is largely because Reddit generally avoids intervening in communities, while occasionally banning subreddits with egregious behavior (REF R3).
+Several Reddit communities, including \texttt{Incels} (REF R5), \texttt{FatPeopleHate} (REF R4), and \texttt{NoNewNormal} (REF R6) that produce hateful, harassing, or misleading content, have also been banned after significant backlash.
+
+\par Reddit has also been responsible for sensationalizing crime.
+In one notable example, Reddit users attempted to solve the identity of the 2013 Boston Marathon Bombers (REF R9).
+Reddit users believed that through community effort and brainstorming, the Reddit community could catch the killers quicker than the authorities.
+After the users performed their investigation, they believed that they had correctly identified the suspect and engaged in harassment of those related to him (REF R9).
+Ultimately, the Reddit users had identified the incorrect perpetrator.
+An embarrassing moment to many Reddit users, the incident nonetheless is important in showing how the fear of crime, and how social media platforms perpetrate this fear, can help radicalize individuals (REF).
 
@@
 \subsection{Reddit Data}
-\par The Reddit dataset contains posts from the subreddits of the 384 MSAs of the United States as of March 2020 \cite{censusmetro}.
+\par The Reddit dataset contains posts from the subreddits of the principal cities of the 384 MSAs of the United States as of March 2020 \cite{censusmetro}.
 From this list of subreddits, we scrape and store all posts that users submit.

### 2022-07-03 paper/main.tex
mostly done

@@
 \par While Urban Areas are an effective method of measuring the true sizes of cities, they are difficult to map and obtain statistics on.
-Their shapes are generally compact and do not have any sort of uniform, governing body.
+Their shapes are generally compact and do not have any sort of uniform governing body.
 To alleviate these issues, we choose Metropolitan Statistical Areas (MSAs) as our scale.
@@
 In this way, we gain the population measurement accuracy of UAs with the ease of data access from state-defined municipalities.
-MSAs also lump together similar, nearby cities, such as New York, Newark, and Jersey City, to avoid redundant analysis.
+MSAs also lump together nearby cities, such as New York, Newark, and Jersey City, to avoid redundant analysis.
 As of March 2020, there are 384 Metropolitan Statistical Areas (REF), each with a corresponding Reddit community.
 
-\subsection{Geography and the Internet}
-
-% TODO
+\subsection{Geography and Social Media}
+
+\par When analyzing our selected Reddit communities, we need to consider the geospatial aspects of social media.
+There is no barrier preventing someone from, for example, Los Angeles from posting in a New York City community.
+(REF) measure the nature of geographic social networks.
+They compared the geospatial proximity of graph-connected users on four social media sites.
+They found that sites, such as FourSquare, that had an explicitly nature had a higher degree of locality.
+However, sites that focused more on general information exchanges showed less geographic clustering.
+The Reddit communities we are analyzing hold an interesting space between these two categories; they are both tied to place and detached from it.
+There is not a geographic component stopping a user from posting to a distant community, but the geospatial nature of the community itself can lead to geographic clustering.
 
@@
 However, the overlap with several New York City-related communities indicates that many of the crime posters have some relation to the city itself.
+When compared to non-crime posters, crime posters exhibit less of a sense of locality.
+Nine of the ten communities that non-crime posters have strong overlap with are explicitly related to New York City, while only seven of the ten communities that crime posters overlap with are geospatially defined.
 
 \par While the two types of posters share some subreddits, their political community overlap is fairly different.
-To identify political subreddits, we derive the methodology from (REF).
+To identify political subreddits, we derive the methodology from (REF - from jeremy).
 Table \ref{table:table-8} shows the political subreddits with the largest amount of overlap.
@@
 Non-crime posters are active in politically moderate communities such as \texttt{tuesday} and \texttt{neoliberal}, as well as \texttt{VoteDem}, which supports the Democratic Party.
+Crime posting users tend to be more active in political communities, with their top three overlapping political subreddits ranking 19th, 23rd, and 32nd.
+Non-crime posting users' highest overlapping political communities rank 21st, 47th, and 77th.
 
@@
 They post about crime frequently, as indicated by their significant overlap with crime discussion specific communities.
-However, they are often local to the communities in which they post, as they have significant overlap to location specific hobby and sport communities.
+However, they are often somewhat local to the communities in which they post, as they have significant overlap to location specific hobby and sport communities.
+Despite this, crime posters have a smaller degree of overlap compared to non-crime posters.
 Lastly, those that post about crime are more active in conservative political communities than those who don't post about crime.
@@
 Furthermore, we have found that the users that make submissions about crime are significantly more negative in their posting and commenting style than those that post about non-crime topics.
-
-\par This paper presents an alternative approach to the measurement of crime discussion and media.
-While there have been several notable papers examining the relationship between crime discussion and traditional media, few have bridged the gap between media, such as newspapers and television stations, and modern social media networks, such as Reddit.
+By measuring community overlap, we have found that these users are generally local to the communities they post in, although to a lesser degree than non-crime posters.
 

### 2022-07-05 paper/main.tex
citations

@@
 % For the references
-\usepackage[sorting=none]{biblatex}
+\usepackage[sorting=nty]{biblatex}
 \addbibresource{References.bib}
@@
 All states are broken down into counties, but differ in how counties are partitioned.
-For example, New York breaks down counties into towns, cities, and villages (REF), while North Dakota only subdivides counties into cities, with excluded areas remaining unincorporated (REF).
+For example, New York breaks down counties into towns, cities, and villages, while North Dakota only subdivides counties into cities, with excluded areas remaining unincorporated.
 In this way, we can think of city limits and city populations as somewhat arbitrary.
@@
 \par The Census Bureau provides several statistical area definitions to normalize city population and sizes.
-The first and most accurate definition is for Urban Areas (UAs) and Urban Clusters (UCs).
+The first and most accurate definition is of Urban Areas (UAs) and Urban Clusters (UCs).
 UAs are dense clusters of people that house over 50,000 people.
-UCs are similarly measured dense clusters of people with between 2,500 and 50,000 people.
-UAs and UCs are computed by first identifying a dense cluster of census blocks, the smallest census geography (REF).
-From here, the UA or UC snakes off from the central core to include housing that fits the density requirements in less dense census blocks (REF).
+UCs are similarly measured dense clusters of people with between 2,500 and 50,000 residents.
+UAs and UCs are computed by first identifying a dense cluster of census blocks, the smallest census geography.
+From here, the UA or UC snakes off from the central core to include housing that fits the density requirements in less dense census blocks \cite{censusurban}.
 This process creates the ``true'' city limits, which are unaffected by municipal boundaries.
@@
 To alleviate these issues, we choose Metropolitan Statistical Areas (MSAs) as our scale.
-MSAs consist of the county or counties in which an Urban Area lies, alongside any counties in which 25\% of the population commutes to a core county (REF).
+MSAs consist of the county or counties in which an Urban Area lies, alongside any counties in which 25\% of the population commutes to a core county \cite{censusmetro}.
 In this way, we gain the population measurement accuracy of UAs with the ease of data access from state-defined municipalities.
 MSAs also lump together nearby cities, such as New York, Newark, and Jersey City, to avoid redundant analysis.
-As of March 2020, there are 384 Metropolitan Statistical Areas (REF), each with a corresponding Reddit community.
+As of March 2020, there are 384 Metropolitan Statistical Areas \cite{censusmetro}, each with a corresponding Reddit community.
 
@@
 There is no barrier preventing someone from, for example, Los Angeles from posting in a New York City community.
-(REF) measure the nature of geographic social networks.
+Scellato et al.
+measure the nature of geographic social networks \cite{sscellato}.
 They compared the geospatial proximity of graph-connected users on four social media sites.
-They found that sites, such as FourSquare, that had an explicitly nature had a higher degree of locality.
+They found that sites, such as FourSquare, that had an explicitly geographic nature had a higher degree of locality.
 However, sites that focused more on general information exchanges showed less geographic clustering.
@@
 % REFS:
-% https://books.google.com/books?id=BmwuDwAAQBAJ&lpg=PP1&ots=_PlVBghHER&dq=media%20and%20crime&lr&pg=PP1#v=onepage&q=media%20and%20crime&f=false
-% https://doi.org/10.1177/0002716295539001011
-% https://doi.org/10.1177/0002764296039004003
-% https://doi.org/10.1177/19401612211020929
-% https://www.cambridge.org/core/books/television-and-its-viewers/83C017F8F8416B5D5F2716EBE5D354BF
-% http://personal.psu.edu/exs44/597b-Comm&Crime/Wilson-Kelling-Broken%20Windows.pdf
-% https://researchgate.net/profile/Tracey-Meares-2/publication/268224149_The_Law_and_Social_Science_of_Stop_and_Frisk/links/54665ea60cf25b85d17f6112/The-Law-and-Social-Science-of-Stop-and-Frisk.pdf
-% https://oxford.universitypressscholarship.com/view/10.1093/acprof:oso/9780195369083.001.0001/acprof-9780195369083
+
 % https://policycommons.net/artifacts/1817184/news-consumption-across-social-media-in-2021/2554124/
@@
 \par Traditional media, such as television, newspapers, magazines, and radio, have long been intertwined with a fascination for crime.
-Live manhunts for people such as OJ Simpson (REF 1) and the Boston Bombers (REF ?) have captured and enthralled viewers and readers.
+Live manhunts for suspects such as OJ Simpson \cite{yjewkes} and the Boston Bombers (REF ?) have captured and enthralled viewers and readers.
 However, while high-profile cases garner much of the attention, local and lower-profile cases often inhabit newspaper columns and television segments.
 It is with these cases that people grow uneasy with the sense of public safety in their community.
-A flurry of reporting on violent acts can increase worry, stress, and fear that crime is rising, even if the documented crime statistics show that crime has not increased (REF 3).
+A flurry of reporting on violent acts can increase worry, stress, and fear that crime is rising, even if the documented crime statistics show that crime has not increased \cite{lheath}.
 
 \par An increase in a fear of crime can have implications beyond elevated negative emotions.
-Fear of crime has far-reaching political social (REF 1), (REF ?), and institutional (REF 2) impacts.
-Belief in excessive amounts of crime can lead to loss of community cohesion (REF 3).
-(REF 3) found that as television news media consumption increased, distrust both in the local community and the world ``out there'' increased.
+Fear of crime has far-reaching political, social \cite{yjewkes}, and institutional \cite{vsacco} impacts.
+Belief in excessive amounts of crime can lead to loss of community cohesion \cite{lheath}.
+Heath and Gilbert found that as television news media consumption increased, distrust both in the local community and the world ``out there'' increased \cite{lheath}.
 Additionally, media creators often sensationalized stories, turning unfortunate incidents into grim spectacles.
@@
 
-\par (REF 4) describes how the prevalence of crime discussion affected the 2016 presidential election in the United States.
-The authors found that voters who consumed more television in turn consumed more campaign advertisements, of which many were about issues such as crime and violence.
-Frequent crime media consumers predict crime and violence issues to be worse than they really are (REF 5).
+\par Liu et al.
+describe how the prevalence of crime discussion affected the 2016 presidential election in the United States \cite{jliu}.
+The authors found that voters who consumed more television in turn consumed more campaign advertisements.
+About 15\% of campaign advertisements were about issues such as crime and violence.
+Frequent crime media consumers predict crime and violence issues to be worse than they really are \cite{jshanahan}.
 Furthermore, the authors found that excessive crime reporting and media exposure had impacts on voting patterns; those that believed crime to be worse tended to vote for more conservative candidates.
@@
 \par Worry of crime victimization can lead to the creation of institutional policies meant to combat the perceived threat.
-One notable example is the idea of Broken Windows Theory (REF 6) and a practice that stemmed from its development, known as stop and frisk (REF 7).
-Broken Windows Theory states that visible signs of crime and disorder lead to further crimes and disorder (REF 6).
+One notable example is the idea of Broken Windows Theory \cite{jwilson} and a practice that stemmed from its development, known as stop and frisk \cite{tmeares}.
+Broken Windows Theory states that visible signs of crime and disorder lead to further crimes and disorder \cite{jwilson}.
 Essentially, the theory states that ignoring minor criminal incidents can lead to more frequent and serious issues.
-Acting on this theory, the New York Police Department instituted a stop and frisk policy, in which police officers temporarily detained civilians suspected of carrying illegal objects (REF 7).
+Acting on this theory, the New York Police Department instituted a stop and frisk policy, in which police officers temporarily detained civilians suspected of carrying illegal objects \cite{tmeares}.
 The effectiveness of the policy, while believed to be effective at the time, has since come under scrutiny.
-Researchers found that only 6\% of stops resulted in arrests (REF 7) and that there is no clear proof that stop and frisk contributed to the decline in crime in New York City (REF 8).
-Stop and frisk was removed as a policy in 2013 when it was deemed unconstitutional (REF 7).
+Researchers found that only 6\% of stops resulted in arrests \cite{tmeares} and that there is no clear proof that stop and frisk contributed to the decline in crime in New York City \cite{dweisburd}.
+Stop and frisk was removed as a policy in 2013 when it was deemed unconstitutional \cite{tmeares}.
 

### 2022-07-05 paper/main.tex
more citations

@@
 \par Crime has long shaped people's lives.
-The fear of crime has inspired historical events (REF), shaped elections (REF), and motivated social movements (REF).
-While fear of crime has occurred organically throughout history, some people or groups have elevated crime cases for political or monetary gain (REF).
-The media is one such group that potentially seeks to gain from crime discussion.
-The relationship between the media and perceptions of crime has been the subject of many studies in fields such as sociology and criminology (REF).
-Through mediums such as television (REF) and print (REF), researchers have long analyzed how the prevalence of crime reporting might affect consumer's perceptions of public safety.
-
-\par While traditional media such as television and newspapers are frequently the subject of research, they have become increasingly less relevant.
-As traditional media declines, social media, such as Twitter, Facebook, and Reddit, has risen in its place.
-As a result, an increasing number of people consume news through social media (REF), which includes topics such as crime.
-However, social media is not without its flaws.
-Due to the free and open nature of who can post on social media, submissions containing misinformation (REF) and manipulation of content (REF) have remained a challenge for social media companies to reign in.
+The fear of crime has inspired historical movements \cite{pmieszkowski} and shaped elections \cite{jliu}.
+While fear of crime has occurred organically throughout history, some have sought to gain politically or monetarily from a saturation of worry.
+One method in which this happens is through the use of media \cite{vsacco}.
+Through mediums such as television \cite{jshanahan} and print \cite{lheath}, researchers have long analyzed how the prevalence of crime reporting might affect consumer's perceptions of public safety.
+
+\par While traditional media, such as television and newspapers, are frequently the subject of crime-relationship research, they have grown increasingly irrelevant.
+As traditional media declines \cite{rnielsen}, social media, such as Twitter, Facebook, and Reddit, has risen in its place.
+Due to this shift in media consumption patterns, an increasing number of people receive news through social media \cite{hkwak}, including stories that focus on crime.
+However, social media faces some flaws not found in the traditional media landscape.
+Due to the free and open nature of who can post on social media, submissions containing misinformation \cite{kognyanova} and manipulation of content \cite{aarif} have remained a challenge for social media companies to reign in.
 
@@
 Specifically, we examine how crime discussion takes shape on the 384 communities, known as subreddits, that represent the Metropolitan Statistical Areas of the United States.
-To measure crime discussion, we have developed a Reddit scraper to fetch all of the posts from the 384 communities.
-We have also developed techniques to identify posts that discuss crime while minimizing false positives.
+To measure crime discussion, we have developed a Reddit scraper to fetch submitted posts from the 384 selected subreddits.
+We then perform textual analysis techniques to identify posts that discuss crime while minimizing false positives.
 We analyze the data collected by the scraper to determine a community's level of crime discussion in comparison to its population, voting patterns, and documented crime rate.
@@
 First, we are collecting data that pertains to the United States.
+Much research has focused on the relationship between crime and media specifically within the United States.
+The United States Census Bureau also provides plentiful contextual and reference data.
 Second, in a general sense, we want to measure at a city-level scale.
@@
 All states are broken down into counties, but differ in how counties are partitioned.
-For example, New York breaks down counties into towns, cities, and villages, while North Dakota only subdivides counties into cities, with excluded areas remaining unincorporated.
+For example, New York breaks down counties into towns and cities, while North Dakota only subdivides counties into cities, with excluded areas remaining unincorporated.
 In this way, we can think of city limits and city populations as somewhat arbitrary.
 There is no consistent, uniform definition, so cities should not be compared to each other.
-To equalize these differences, we use statistical area definitions provided by the United States Census Bureau.
+To best equalize these differences, we use statistical area definitions provided by the United States Census Bureau.
 
@@
 In this way, we gain the population measurement accuracy of UAs with the ease of data access from state-defined municipalities.
-MSAs also lump together nearby cities, such as New York, Newark, and Jersey City, to avoid redundant analysis.
 As of March 2020, there are 384 Metropolitan Statistical Areas \cite{censusmetro}, each with a corresponding Reddit community.
@@
 \par When analyzing our selected Reddit communities, we need to consider the geospatial aspects of social media.
-There is no barrier preventing someone from, for example, Los Angeles from posting in a New York City community.
+In some sites, specific geographic location is intrinsic to the functionality of the product, whereas in others, anyone can browse a community for somewhere far away.
+For example, on Reddit there is no barrier preventing someone from, for example, Los Angeles from posting in a New York City community.
 Scellato et al.
-measure the nature of geographic social networks \cite{sscellato}.
-They compared the geospatial proximity of graph-connected users on four social media sites.
-They found that sites, such as FourSquare, that had an explicitly geographic nature had a higher degree of locality.
-However, sites that focused more on general information exchanges showed less geographic clustering.
-The Reddit communities we are analyzing hold an interesting space between these two categories; they are both tied to place and detached from it.
-There is not a geographic component stopping a user from posting to a distant community, but the geospatial nature of the community itself can lead to geographic clustering.
+measure the geographic nature of social networks through the comparison of geospatial proximity of graph-connected users on four social media sites \cite{sscellato}.
+They found that sites, such as FourSquare, that had an explicitly geographic nature produced a higher degree of locality.
+However, sites that focused more on general information exchanges, such as Twitter, showed less geographic clustering.
+
+\par The Reddit communities we are analyzing hold an interesting space between these two categories; they are both tied to place and detached from it.
+There is no geographic component stopping a user from posting to a distant community, but the geospatial nature of the community itself can lead to geographic clustering.
+In this way, we must determine if those posting in a certain community are truly local.
 
@@
 
-% REFS:
-
-% https://policycommons.net/artifacts/1817184/news-consumption-across-social-media-in-2021/2554124/
-% https://papers.ssrn.com/sol3/papers.cfm?abstract_id=2771080
-
-\par Traditional media, such as television, newspapers, magazines, and radio, have long been intertwined with a fascination for crime.
-Live manhunts for suspects such as OJ Simpson \cite{yjewkes} and the Boston Bombers (REF ?) have captured and enthralled viewers and readers.
+\par Traditional media, such as television, newspapers, magazines, and radio, has long been intertwined with a fascination for crime.
+Live manhunts for suspects such as OJ Simpson \cite{yjewkes} and the Boston Bombers \cite{aspeckhard} have captured and enthralled viewers and readers.
 However, while high-profile cases garner much of the attention, local and lower-profile cases often inhabit newspaper columns and television segments.
@@
 \par An increase in a fear of crime can have implications beyond elevated negative emotions.
-Fear of crime has far-reaching political, social \cite{yjewkes}, and institutional \cite{vsacco} impacts.
-Belief in excessive amounts of crime can lead to loss of community cohesion \cite{lheath}.
-Heath and Gilbert found that as television news media consumption increased, distrust both in the local community and the world ``out there'' increased \cite{lheath}.
+Fear of crime has far-reaching social\cite{lheath}, political \cite{yjewkes}, and institutional \cite{vsacco} impacts.
+Belief in excessive amounts of crime can lead to loss of community cohesion; Heath and Gilbert found that as television news media consumption increased, distrust both in the local community and the world ``out there'' increased \cite{lheath}.
 Additionally, media creators often sensationalized stories, turning unfortunate incidents into grim spectacles.
@@
 Social media, which originally started as a method of connecting with friends and family, has grown and evolved beyond its humble beginnings.
-Social media sites, such as Twitter, are now significant sources of new for many Americans (REF - LR: What is twitter?).
-(REF 9) found that nearly half of Americans consume their news from social media sites like Twitter, Facebook, and Reddit.
+Social media sites, such as Twitter, are now significant sources of new for many Americans \cite{hkwak}.
+Walker and Masta found that nearly half of Americans consume their news from social media sites like Twitter, Facebook, and Reddit \cite{pewresearch}.
 This trend coincides with the decline of traditional media.
-Printed media, such as newspapers and magazines, as well as televised media, has consistently declined since the explosive growth of the Internet (REF 10).
+Printed media, such as newspapers and magazines, as well as televised media, have consistently declined since the explosive growth of the Internet \cite{rnielsen}.
 Despite this, research on social media remains sparse.
 
-% Paragraph about relevant paper
-
-(REF) detail the ecosystem of crime discussion on Twitter.
+Curiel et al.
+detail the ecosystem of crime discussion on Twitter \cite{curiel}.
 Specifically, they look at how often crime discussion appears in Tweets posted from users in Latin American countries.
@@
 
-(REF) introduce an interesting observation: some of the crime-related Tweets are highly sensationalized or completely untrue.
+Curiel et al.
+introduce an interesting observation: some of the crime-related Tweets are highly sensationalized or completely untrue \cite{curiel}.
 In this way, social media differs from traditional media.
-Traditional media acts as a gatekeeper (REF 2), where only select stories and viewpoints emerge and some degree of factchecking generally exists (REF ?).
+Traditional media acts as a gatekeeper, where only select stories and viewpoints emerge and factchecking generally exists in mainstream publications \cite{vsacco}.
 Social media, on the other hand, allows for a more diverse set of viewpoints and opinions.
-However, as there is generally a limited amount of moderation (REF ?) on social media platforms, blatantly false stories can spread across sites (REF).
+However, as moderation policies vary \cite{szannettou} on social media platforms, blatantly false stories can spread across sites if left unchecked.
 This proliferation of misinformation has become increasingly impactful in the United States.
-It has affected important events in recent American history, including presidential elections (REF ?) and the the response to the Covid-19 pandemic (REF ?).
-Despite attempts to curb the spread of misinformation on social media (REF ?), falsehoods and panics continue to spread across the web.
+It has affected important events in recent American history, including presidential elections \cite{jliu} and the the response to the Covid-19 pandemic \cite{amian} \cite{ftahmsabi}.
+Without intervention, falsehoods and panics continue to spread across the web.
 

### 2022-07-13 paper/main.tex
final draft

@@
 
-THESIS OR DISSERTATION TITLE IS CENTERED AND IN ALL CAPS.\\
-THE FIRST LINE OF THE TITLE SHOULD BE TWO INCHES FROM.\\
-THE TOP OF THE PAGE. SINGLE-SPACED.
+CRIME AND SOCIAL MEDIA: \\
+THE GEOGRAPHY OF CRIME DISCUSSION ON REDDIT \\
 
@@
 
-AUTHOR NAME IN ALL CAPITAL LETTERS
+SEAN KUNZ
 
@@
 
-B\textit{X}, College of University, YYYY\\
-M\textit{X}, College of University, YYYY
+BS, Binghamton University, 2020\\
 
@@
 
-SPECIFY DISSERTATION OR THESIS
+THESIS
 
@@
 Submitted in partial fulfillment of the requirements for\\
-the degree of Name of Degree in Major\\
+Master of Science in Computer Science\\
 in the Graduate School of\\
@@
 State University of New York\\
-YYYY
+2022
 
@@
 
-\centerline{\copyright\ Copyright by Full Legal Name of Author YYYY}
+\centerline{\copyright\ Copyright by Sean Kunz 2022}
 
@@
 \centerline{Accepted in partial fulfillment of the requirements for}
-\centerline{the degree of Name of Degree in Major}
+\centerline{Master of Science in Computer Science}
 \centerline{in the Graduate School of}
@@
 \centerline{State University of New York}
-\centerline{YYYY}
+\centerline{2022}
 
@@
 \vbox to 4.25truein{}
-\centerline{The dedication is optional. Type your dedication here, centered on the page.}
+\centerline{Dedicated to my friends, family, and all those who helped me along the way}
 
@@
 
-UA  Urbanized Area
-
-UC  Urbanized Cluster
+UA  Urban Area
+
+UC  Urban Cluster
 
@@
 In this work, we analyze the discussion of crime on the social media website Reddit.
-Specifically, we examine how crime discussion takes shape on the 384 communities, known as subreddits, that represent the Metropolitan Statistical Areas of the United States.
-To measure crime discussion, we have developed a Reddit scraper to fetch submitted posts from the 384 selected subreddits.
+Specifically, we examine how crime discussion takes shape on the 384 communities that represent the Metropolitan Statistical Areas of the United States.
+To measure crime discussion, we have developed a Reddit scraper to fetch submitted posts from the 384 selected communities.
 We then perform textual analysis techniques to identify posts that discuss crime while minimizing false positives.
@@
 Social media, which originally started as a method of connecting with friends and family, has grown and evolved beyond its humble beginnings.
-Social media sites, such as Twitter, are now significant sources of new for many Americans \cite{hkwak}.
+Social media sites, such as Twitter, are now significant sources of news for many Americans \cite{hkwak}.
 Walker and Masta found that nearly half of Americans consume their news from social media sites like Twitter, Facebook, and Reddit \cite{pewresearch}.
@@
 
-\par While Facebook (REF ?) and Twitter (REF ?) face much of the backlash from outrage directed towards online misinformation, smaller websites, like Reddit, play a role in the distribution of sensationalized stories and misinformation as well.
+\par While Facebook \cite{sphadke} and Twitter \cite{ftahmsabi} have many times been the subject of backlash directed towards online misinformation, smaller websites, like Reddit, play a role in the distribution of sensationalized stories and misinformation as well.
 Reddit communities, also known as subreddits, allow users to post self-made content or link content from other parts of the web.
@@
 In this way, misinformation can seep into communities, as there are differing levels of moderation among subreddits.
-To combat rouge communities and moderators, Reddit has moved to ban certain subreddits that consistently break rules (REF R1).
+To combat rouge communities and moderators, Reddit has moved to ban certain subreddits that consistently break sitewide rules \cite{mribeiro}.
 
@@
 One such subreddit is known as \texttt{The\_Donald} (TD).
-TD, which acted as the support community for former President Donald Trump, spread unsubstantiated conspiracy theories, such as Pizzagate (REF R2) and engaged in harassment of other communities on the website (REF - extracting inter...).
-TD was eventually quarantined and banned from the site, leading users to create their own Reddit offshoot website (REF R1).
-However, TD spread misinformation with little intervention for the nearly five years that it survived on the site (REF R1).
-This is largely because Reddit generally avoids intervening in communities, while occasionally banning subreddits with egregious behavior (REF R3).
-Several Reddit communities, including \texttt{Incels} (REF R5), \texttt{FatPeopleHate} (REF R4), and \texttt{NoNewNormal} (REF R6) that produce hateful, harassing, or misleading content, have also been banned after significant backlash.
+TD, which acted as the support community for former President Donald Trump, spread unsubstantiated conspiracy theories, such as Pizzagate \cite{aohlheiser} and engaged in harassment of other communities on the website \cite{sdatta}.
+TD was eventually quarantined and banned from the site, leading users to create their own Reddit offshoot website \cite{mribeiro}.
+However, TD spread misinformation with little intervention for the nearly five years that it survived on the site \cite{mribeiro}.
+This is largely because Reddit generally avoids intervening in communities, while occasionally banning subreddits with egregious behavior \cite{hmohammad}.
+Several Reddit communities, including \texttt{Incels} \cite{mribeiro2}, \texttt{FatPeopleHate} \cite{echand}, and \texttt{NoNewNormal} \cite{cdavies} that produce hateful, harassing, or misleading content, have also been banned after significant backlash.
 
 \par Reddit has also been responsible for sensationalizing crime.
-In one notable example, Reddit users attempted to solve the identity of the 2013 Boston Marathon Bombers (REF R9).
+In one notable example, Reddit users attempted to solve the identity of the 2013 Boston Marathon Bombers \cite{lpotts}.
 Reddit users believed that through community effort and brainstorming, the Reddit community could catch the killers quicker than the authorities.
-After the users performed their investigation, they believed that they had correctly identified the suspect and engaged in harassment of those related to him (REF R9).
+After the users performed their investigation, they believed that they had correctly identified the suspect and engaged in harassment of those related to him \cite{lpotts}.
 Ultimately, the Reddit users had identified the incorrect perpetrator.
-An embarrassing moment to many Reddit users, the incident nonetheless is important in showing how the fear of crime, and how social media platforms perpetrate this fear, can help radicalize individuals (REF).
+An embarrassing moment to many Reddit users, the incident nonetheless is important in showing how the fear of crime, and how social media platforms perpetrate this fear, can help radicalize individuals.
 
@@
 These keywords were derived from actions that constitute violent crime and their synonyms, as well as generic crime-related words.
-In total, 46 keywords and their derivatives are used.
+In total, 124 keywords are used.
 If the regular expression returns a hit, a flag is raised in the database denoting that the post is about crime.
@@
 \par Due to the nature of text analysis, a number of false positives might be considered, while some false negatives go undetected.
-False negatives can be hard to detect, as they include dog-whistles, local-dependent terms, and ambiguous references (REF).
-Certain posters may choose to keep their posts ambiguous so as to keep their intentions visible to only a small group (REF).
-
-\par To determine the rate of false positives, we analyze a sample of scraped posts.
+False negatives can be hard to detect, as they include dog-whistles, local-dependent terms, and ambiguous references \cite{curiel}.
+Certain posters may choose to keep their posts ambiguous so as to keep their intentions visible to only a small group \cite{aaddawood}.
+To determine the rate of false positives, we analyze a sample of scraped posts.
 We look for phrases such as ``I shot a picture'' that do not relate to crime, but contain a crime-related keyword.
 Of a sample of 400 posts, we find that 36 posts do not relate to crime, for an accuracy rate of 91\%.
-Similar analysis done on the social media site reached a rate of 66\% \cite{curiel}.
+Similar analysis done on the social media site Twitter reached a rate of 66\% accuracy \cite{curiel}.
 
@@
 The population cutoffs are 1,000,000, 500,000, and 200,000.
-The large population contains 56 members, the medium bin contains 54 members, the small bin contains 113 members, and the very small bin contains 161 members.
+The large population bin contains 56 members, the medium bin contains 54 members, the small bin contains 113 members, and the very small bin contains 161 members.
 
 \par Another variable that provides context is the political climate of an MSA.
-For this, we consider the results of the 2020 election (REF) in terms of the percent of the MSA voting Democrat.
+For this calculation, we consider the results of the 2020 election \cite{ap} in terms of the percent of the MSA voting Democrat.
 These values range from a minimum of 20.2\% (Morristown, TN) to a maximum of 80.9\% (Santa Cruz-Watsonville, CA).
@@
 \par A third variable that is considered is the documented violent crime rate of each MSA.
-This data is derived from the FBI's Uniform Crime Reporting statistics (REF) \footnote{Data from the FBI mostly comes from the year that is most recent, 2019.
-However, not all municipalities report information, so there are slight estimations in the data (REF).}.
-These values range from a minimum of 44.3/100,000 (Bangor, ME) to a maximum of 1,397.2/100,000 (Birmingham-Hoover, AL).
+This data is derived from the FBI's Uniform Crime Reporting \cite{ucr} statistics.
+\footnote{Data from the FBI mostly comes from the year that is most recent, 2019.
+However, not all municipalities report information, so there are slight estimations in the data \cite{ucr2}} Documented violent crime rates range from a minimum of 44.3/100,000 (Bangor, ME) to a maximum of 1,397.2/100,000 (Birmingham-Hoover, AL).
+We select violent crime rates for our comparison data because they are less ambiguous than property crimes.
+For example, police departments are less likely to differ in their definition of a homicide compared to criminal mischief.
 Documented crime data is also normalized using min-max normalization so that it can be compared to a similarly normalized crime discussion value from the Reddit data.
@@
 This scraper utilizes multiple different tools to gather disparate pieces of data and place them into two datastores.
-This scraper prioritizes resilience to ensure that all posts are accounted for.
-Additionally, the scraper checks for new posts once every hour so that posts can be fetched before a user deletes them or a moderator deletes them.
+The scraper checks for new posts once every hour so that posts can be fetched before a user deletes them or a moderator removes them.
 These communities are generally slow moving, with an average of 111 posts an hour between all 384 subreddits.
@@
 This parameter allows us to take posts that have been created since a given post ID.
-This parameter is especially useful on slower subreddits; without it, we would be performing requests on posts that might be months old.
+The \texttt{after} parameter is especially useful on slower subreddits; without it, we would be fetching posts that might be months old.
 If the cached value does not exist or is not valid, then the most recent hundred posts are gathered.
@@
 The first is a CockroachDB database that acts as a system of record.
-Raw posts are stored here in a simple format: \texttt{id}, \texttt{timestamp}, and \texttt{data}, which is the data retrieved from the Reddit API in JSON format.
+Raw posts are stored here in a simple format: \texttt{id}, \texttt{timestamp}, and \texttt{data}, the last of which is the data retrieved from the Reddit API in JSON format.
 After writing to CockroachDB, the scraper then writes the JSON data from Reddit to ElasticSearch.
@@
 Containerization allows the tool, as well as the databases, to run in a clean, isolated environment without worrying about being choked out by other processes.
-Additionally, the tool-container is scheduled by Kubernetes to allow for a higher degree of availability and resilience.
+Additionally, the scraper-container is scheduled by Kubernetes to allow for a higher degree of availability and resilience.
 If something unexpected occurs and the tool goes down, it will simply be restarted by Kubernetes.
@@
 \par In total, the Reddit scraper gathered 161,166 posts between 384 subreddits.
-Posts were collected between April 5th, 2022 to May 31, 2022.
+Posts were collected between April 5th, 2022 and May 31, 2022.
 Table \ref{table:table-1} details the ten most active subreddits of those monitored.
@@
 \begin{table}[h!]
-    \centering
     \small
@@
     %\begin{tabu} to 1.0\textwidth {| *{3}{c|} }
-    \begin{tabular}{| c | c | c |}
+    \begin{tabular}{| c | r | r |}
     \hline
@@
 While expected, some of the most notable MSAs were not included, such as New York-Newark-Jersey City, NJ-NJ-PA and Los Angeles-Long Beach-Anaheim, CA, which have populations of 20,140,470 and 13,200,998, respectfully.
-One possible explanation for these exclusions is the fact that there is no uniform, consistent moderation policy among subreddits (REF).
-For example, some subreddits automatically filter out all posts and manually approve them, or they disallow certain types of posts (REF - nyc n chicago rules).
+One possible explanation for these exclusions is the fact that there is no uniform, consistent moderation policy among subreddits \cite{sjhaver}.
+For example, some subreddits automatically filter out all posts and manually approve them, or they disallow certain types of posts \cite{rnyc}.
 Subreddits with more laissez-faire moderation policies will have more posts simply because they are not removing a mass of posts that could be considered redundant or irrelevant.
@@
 \par The list of most active MSAs when normalizing by population also share some common traits.
-These MSAs are generally politically liberal (REF) and have large college age populations (REF).
-Essentially, these areas have large populations of people that fall under Reddit's main demographic (REF) and, as a result, have correspondingly active communities.
+These MSAs are generally politically liberal \cite{ap} and have large college age populations \cite{age}.
+Essentially, these areas have large populations of people that fall under Reddit's main demographic \cite{wsattelberg} and, as a result, have correspondingly active communities.
 
@@
 Higher documented crime rates can lead to increased amounts of crime discussion, as crime may affect more members of the community.
-To measure MSA crime rates, we use the FBI's Uniform Crime Reporting Estimates (REF).
+To measure MSA crime rates, we use the FBI's Uniform Crime Reporting Estimates \cite{ucr}.
 The 384 Metropolitan Areas represent a differing level of crime rates, with a high of 1397.2 from Birmingham-Hoover, AL, a low of 44.3 from Bangor, ME, and an average of 380.9 among all MSAs.
@@
 \par From Tables \ref{table:table-3} and \ref{table:table-4}, as well as Figures \ref{fig:map-1} and \ref{fig:map-3}, we can see that MSAs with high reported crime rates do not necessarily have high amounts of crime discussion.
-This includes Metropolitan Areas such as Danville, IL and Farmington, NM.
+Examples include Metropolitan Areas such as Danville, IL and Farmington, NM.
 The same goes for MSAs with low crime rates and low amounts of crime discussion.
@@
 
-\par From the map in Figure \ref{fig:map-3}, we can see that many Metropolitan Areas with high documented crime rates lie in the South and Midwest (REF).
+\par From the map in Figure \ref{fig:map-3}, we can see that many Metropolitan Areas with high documented crime rates lie in the South and Midwest \cite{ucr}.
 However, many these MSAs have low amounts of crime discussion.
@@
 \par Table \ref{table:table-5} displays the 15 highest and lowest scoring MSAs for the crime discussion to crime rate ratio.
-A full listing can be found in Appendix (REF).
+A full listing can be found in Appendix A.
 Of the highest scoring MSAs, large and very small Metropolitan Areas are over-represented, while all population sizes are represented among the lowest scoring Metropolitan Areas.
@@
 In this case, we measure the mean polarity score of users who post about crime and compare it to the mean polarity score of users who don't post about crime.
-A lower polarity means that the input data is more negative, while higher scores mean that the sentiment is more positive (REF).
+A lower polarity means that the input data is more negative, while higher scores mean that the sentiment is more positive \cite{wmedhat}.
 This can indicate the potential nature of a poster; if their polarity score is low, then they are a consistently negative voice in the community.
@@
 Examples include location identity and political affiliation.
-To measure this, we use the Jaccard Index.
-The Jaccard index can be defined as:
-
-(REF)
+To measure this, we use the Jaccard Index \cite{sfletcher}.
+The Jaccard Index takes the following form, where $0 \leq J(A, B) \leq 1$ and A and B represent subreddits:
+
+\[J(A, B) = \frac{|A \cap B|}{|A \cup B|}\]
 
@@
     %\begin{tabu} to 1.0\textwidth {| *{3}{c|} }
-    \begin{tabular}{| c | c | c | c |}
+    \begin{tabular}{| c | r | c | r |}
     \hline
@@
 \par While the two types of posters share some subreddits, their political community overlap is fairly different.
-To identify political subreddits, we derive the methodology from (REF - from jeremy).
+To identify political subreddits, we derive the methodology from Rajadesingan et al.
+\cite{araja}.
 Table \ref{table:table-8} shows the political subreddits with the largest amount of overlap.
@@
 \par While this paper provides a first look at the crime discussion dynamics on Reddit, there are several paths that continued research could explore.
-One pathway of future work on the relationship between crime discussion and social media could include a more in-depth analysis of users that post about crime beyond the sample that we took.
+One pathway of future work on the relationship between crime discussion and social media could include a more in-depth analysis of users that post about crime beyond the sample of \texttt{nyc} users that we looked at.
 Another approach could be applying the tool and analysis used on Reddit to other social media platforms, such as Facebook or Nextdoor, to determine if this phenomenon is Reddit-specific.
@@
 
-\begin{longtable}{| p{.6\textwidth} | p{.15\textwidth} | p{.15\textwidth} |}
+\begin{longtable}{|p{0.5\textwidth}|r|r|}
     %\begin{tabu} to 1.0\textwidth {| *{3}{c|} }
@@
     Yuma, AZ Metro Area & 0.86 & -0.15 \\ \hline
-    \caption{Metropolitan Areas and their subreddits}
+    \caption{Metropolitan Areas}
 	\label{table:app-a}
 \end{longtable}
-
-% Appendix A - Metro, subreddit
-% Appendix B - Metro, population, pop class, Pcrime rate
-% Appendix C - Metro, percent dem, pol class, pcrime rate
-% Appendix D - Metro, normalized cr, normalized pcr
-% Appendix E - Keywords
-
-\newpage
-\chapter*{Notes}
-\addcontentsline{toc}{chapter}{Notes}
 

### 2022-07-22 paper/main.tex
more corrections on paper

@@
 While fear of crime has occurred organically throughout history, some have sought to gain politically or monetarily from a saturation of worry.
-One method in which this happens is through the use of media \cite{vsacco}.
+The calculated use of media can exacerbate this fear \cite{vsacco}.
 Through mediums such as television \cite{jshanahan} and print \cite{lheath}, researchers have long analyzed how the prevalence of crime reporting might affect consumer's perceptions of public safety.
@@
 Due to this shift in media consumption patterns, an increasing number of people receive news through social media \cite{hkwak}, including stories that focus on crime.
-However, social media faces some flaws not found in the traditional media landscape.
+However, social media faces some challenges not found in the traditional media landscape.
 Due to the free and open nature of who can post on social media, submissions containing misinformation \cite{kognyanova} and manipulation of content \cite{aarif} have remained a challenge for social media companies to reign in.
@@
 In this work, we analyze the discussion of crime on the social media website Reddit.
-Specifically, we examine how crime discussion takes shape on the 384 communities that represent the Metropolitan Statistical Areas of the United States.
-To measure crime discussion, we have developed a Reddit scraper to fetch submitted posts from the 384 selected communities.
-We then perform textual analysis techniques to identify posts that discuss crime while minimizing false positives.
-We analyze the data collected by the scraper to determine a community's level of crime discussion in comparison to its population, voting patterns, and documented crime rate.
+Specifically, we examine how crime discussion takes shape on 384 unique communities in the United States.
+To measure crime discussion, we have developed a Reddit crawler to fetch submitted posts from the 384 selected communities.
+We then utilize textual analysis techniques to identify posts that discuss crime while minimizing false positives.
+We analyze the data collected by the crawler to determine a community's level of crime discussion in comparison to its population, voting patterns, and documented crime rate.
 Lastly, we dive into the posting histories of users who post to Reddit's New York City community to identify any further trends or patterns.
@@
 
-\subsection{Scale}
+\subsection{Scope}
 
@@
 In this way, we can think of city limits and city populations as somewhat arbitrary.
-There is no consistent, uniform definition, so cities should not be compared to each other.
-To best equalize these differences, we use statistical area definitions provided by the United States Census Bureau.
+There is no consistent, uniform definition, so one should be careful when comparing cities for analysis purposes.
 
@@
 
-\par The Census Bureau provides several statistical area definitions to normalize city population and sizes.
-The first and most accurate definition is of Urban Areas (UAs) and Urban Clusters (UCs).
+\par To best equalize differences in city definitions, we use statistical area delineations provided by the United States Census Bureau to normalize city population and sizes.
+The first and most precise definition is of Urban Areas (UAs) and Urban Clusters (UCs).
 UAs are dense clusters of people that house over 50,000 people.
@@
 Scellato et al.
-measure the geographic nature of social networks through the comparison of geospatial proximity of graph-connected users on four social media sites \cite{sscellato}.
+\cite{sscellato} measure the geographic nature of social networks through the comparison of geospatial proximity of graph-connected users on four social media sites.
 They found that sites, such as FourSquare, that had an explicitly geographic nature produced a higher degree of locality.
@@
 
-\par The Reddit communities we are analyzing hold an interesting space between these two categories; they are both tied to place and detached from it.
+\par The Reddit communities we analyze hold an interesting space between these two categories; they are both tied to place and detached from it.
 There is no geographic component stopping a user from posting to a distant community, but the geospatial nature of the community itself can lead to geographic clustering.
@@
 
-\par An increase in a fear of crime can have implications beyond elevated negative emotions.
+\par An increase in fear of crime can have implications beyond elevated negative emotions.
 Fear of crime has far-reaching social\cite{lheath}, political \cite{yjewkes}, and institutional \cite{vsacco} impacts.
@@
 \par Liu et al.
-describe how the prevalence of crime discussion affected the 2016 presidential election in the United States \cite{jliu}.
+\cite{jliu} describe how the prevalence of crime discussion affected the 2016 presidential election in the United States.
 The authors found that voters who consumed more television in turn consumed more campaign advertisements.
-About 15\% of campaign advertisements were about issues such as crime and violence.
-Frequent crime media consumers predict crime and violence issues to be worse than they really are \cite{jshanahan}.
+About 15\% of campaign advertisements covered issues such as crime and violence.
+Frequent crime media consumers assumed crime and violence issues to be worse than they really are \cite{jshanahan}.
 Furthermore, the authors found that excessive crime reporting and media exposure had impacts on voting patterns; those that believed crime to be worse tended to vote for more conservative candidates.
@@
 Acting on this theory, the New York Police Department instituted a stop and frisk policy, in which police officers temporarily detained civilians suspected of carrying illegal objects \cite{tmeares}.
-The effectiveness of the policy, while believed to be effective at the time, has since come under scrutiny.
+The policy, while believed to be effective at the time, has since come under scrutiny.
 Researchers found that only 6\% of stops resulted in arrests \cite{tmeares} and that there is no clear proof that stop and frisk contributed to the decline in crime in New York City \cite{dweisburd}.
@@
 \par While the relationship between traditional media and crime has been thoroughly researched, the relationship between social media and crime has not been as rigorously explored.
-Social media, which originally started as a method of connecting with friends and family, has grown and evolved beyond its humble beginnings.
-Social media sites, such as Twitter, are now significant sources of news for many Americans \cite{hkwak}.
+Social media has grown and evolved beyond its humble beginnings.
+Social media sites, such as Twitter, are now the main source of news for many Americans \cite{hkwak}.
 Walker and Masta found that nearly half of Americans consume their news from social media sites like Twitter, Facebook, and Reddit \cite{pewresearch}.
@@
 Printed media, such as newspapers and magazines, as well as televised media, have consistently declined since the explosive growth of the Internet \cite{rnielsen}.
-Despite this, research on social media remains sparse.
 
 Curiel et al.
-detail the ecosystem of crime discussion on Twitter \cite{curiel}.
+\cite{curiel} detail the ecosystem of crime discussion on Twitter.
 Specifically, they look at how often crime discussion appears in Tweets posted from users in Latin American countries.
@@
 
-% Paragraph about misinformation
-
-Curiel et al.
-introduce an interesting observation: some of the crime-related Tweets are highly sensationalized or completely untrue \cite{curiel}.
+The authors introduce an interesting observation: some of the crime-related Tweets are highly sensationalized postings from a group of ``involved users'' that frequently comment about violence \cite{curiel}.
 In this way, social media differs from traditional media.
@@
 \par The Reddit dataset contains posts from the subreddits of the principal cities of the 384 MSAs of the United States as of March 2020 \cite{censusmetro}.
-From this list of subreddits, we scrape and store all posts that users submit.
+From this list of subreddits, we fetch and store all posts that users submit.
 In total, 161,166 posts were gathered between April 5, 2022 and May 31, 2022.
@@
 These keywords were derived from actions that constitute violent crime and their synonyms, as well as generic crime-related words.
-In total, 124 keywords are used.
+In total, 124 crime-related keywords are used.
 If the regular expression returns a hit, a flag is raised in the database denoting that the post is about crime.
@@
 Certain posters may choose to keep their posts ambiguous so as to keep their intentions visible to only a small group \cite{aaddawood}.
-To determine the rate of false positives, we analyze a sample of scraped posts.
+To determine the rate of false positives, we analyze a sample of stored posts.
 We look for phrases such as ``I shot a picture'' that do not relate to crime, but contain a crime-related keyword.
@@
 \subsection{Contextual Data}
-\par A variety of data were utilized to highlight trends in the Reddit posts.
+\par We utilize a variety of data to highlight trends in the Reddit posts.
 One variable that subreddits are compared to is population size of the MSA.
@@
 \par Another variable that provides context is the political climate of an MSA.
-For this calculation, we consider the results of the 2020 election \cite{ap} in terms of the percent of the MSA voting Democrat.
+For this metric, we consider the results of the 2020 election \cite{ap} in terms of the percent of the MSA voting Democrat.
+In this case, we only document Democrat and Republican votes.
 These values range from a minimum of 20.2\% (Morristown, TN) to a maximum of 80.9\% (Santa Cruz-Watsonville, CA).
@@
 For example, police departments are less likely to differ in their definition of a homicide compared to criminal mischief.
-Documented crime data is also normalized using min-max normalization so that it can be compared to a similarly normalized crime discussion value from the Reddit data.
+Additionally, documented crime data is normalized using the min-max normalization method.
+This method condenses all values in a range between a value of 0 and 1, where 1 is the highest value in the range and 0 is the lowest.
+In doing so, we can compare crime data to a similarly normalized crime discussion value from the Reddit data.
 
 \section{Methods}
-\par We use one main scraper to gather post data from Reddit.
-This scraper utilizes multiple different tools to gather disparate pieces of data and place them into two datastores.
-The scraper checks for new posts once every hour so that posts can be fetched before a user deletes them or a moderator removes them.
+\par We use one main crawler to gather post data from Reddit.
+This crawler utilizes multiple different tools to gather disparate pieces of data and place them into two datastores.
+The crawler checks for new posts once every hour so that posts can be fetched before a user deletes them or a moderator removes them.
 These communities are generally slow moving, with an average of 111 posts an hour between all 384 subreddits.
 
-\par To gather the data, the scraper first sends requests to the Reddit REST API \cite{reddit}.
+\par To gather the data, the crawler first sends requests to the Reddit REST API \cite{reddit}.
 We use the \texttt{new} endpoint for each subreddit to check the most recent posts.
@@
 Raw posts are stored here in a simple format: \texttt{id}, \texttt{timestamp}, and \texttt{data}, the last of which is the data retrieved from the Reddit API in JSON format.
-After writing to CockroachDB, the scraper then writes the JSON data from Reddit to ElasticSearch.
+After writing to CockroachDB, the crawler then writes the JSON data from Reddit to ElasticSearch.
 ElasticSearch provides quick and efficient text analysis that allows for the extraction of certain keywords in post titles and URLs.
 
-\par The scraper and databases run in Docker containers.
+\par The crawler and databases run in Docker containers.
 Containerization allows the tool, as well as the databases, to run in a clean, isolated environment without worrying about being choked out by other processes.
-Additionally, the scraper-container is scheduled by Kubernetes to allow for a higher degree of availability and resilience.
+Additionally, the crawler-container is scheduled by Kubernetes to allow for a higher degree of availability and resilience.
 If something unexpected occurs and the tool goes down, it will simply be restarted by Kubernetes.
@@
 
-\par In total, the Reddit scraper gathered 161,166 posts between 384 subreddits.
+\par In total, the Reddit crawler gathered 161,166 posts between 384 subreddits.
 Posts were collected between April 5th, 2022 and May 31, 2022.
@@
 The darker the shade of green, the more posts discuss crime.
-The average crime discussion percentage lays at 3.5\%.
+The average crime discussion percentage is 3.5\%.
 
@@
 \par From Figure \ref{fig:graph-1}, we can see that as population increases, documented crime rates gradually increase.
-This trend is semi-reflected in the crime discussion data.
+This trend is reflected in the crime discussion data.
 Crime discussion scores are roughly equivalent for the very small, small, and medium buckets.
-However, the large population bucket has a significantly higher crime discussion score than that of the other buckets.
+However, the large population bucket has a much higher crime discussion score than that of the other buckets.
 The large population bucket has a 6\% greater score than the medium population bucket when comparing documented crime data, but the large population bucket has a 56\% greater score than the medium population bucket when comparing crime discussion data.
@@
 \par Figure \ref{fig:cdf-1} shows a cumulative distribution function of the data by population bucket.
-Here, we can see that the smallest value of the class of large populations is the greatest among the four classes, while its largest value is greater than all of the other classes' largest values.
-This relationship remains true throughout most of the distribution, resulting in the large MSAs having the highest mean crime discussion score.
-When looking at the very small MSAs, we can see that some Metropolitan Areas in its category have high average crime discussion.
-However, a significant amount of very small MSAs have no crime discussion at all.
-From the CDF we can see that almost 20\% of very small MSA subreddits have not discussed crime at all.
-The next highest zero crime discussion class is small, with about 8\% of communities not discussing crime.
+Here, we can see that the members of the large population bucket have higher crime discussion scores.
+When looking at the very small MSAs, we notice quite a few outliers.
+We can see that some Metropolitan Areas in this category have among the highest amounts of crime discussion.
+However, almost 20\% of very small MSA subreddits have not discussed crime at all.
+The small bucket has the next highest percentage of subreddits with zero crime discussion, with about 8\% of communities not discussing crime at all.
 
@@
 To measure MSA crime rates, we use the FBI's Uniform Crime Reporting Estimates \cite{ucr}.
-The 384 Metropolitan Areas represent a differing level of crime rates, with a high of 1397.2 from Birmingham-Hoover, AL, a low of 44.3 from Bangor, ME, and an average of 380.9 among all MSAs.
+The 384 Metropolitan Areas represent a differing level of crime rates, with a high of 1,397.2 from Birmingham-Hoover, AL, a low of 44.3 from Bangor, ME, and an average of 380.9 among all MSAs.
 Table \ref{table:table-3} displays the MSAs with the ten highest documented crime rates.
@@
     \small
-    \caption{Most active Metropolitan Areas per population}
+    \caption{MSAs with highest crime rates}
     %\begin{tabu} to 1.0\textwidth {| *{3}{c|} }
@@
     Birmingham-Hoover, AL & 1,397.2 & 2.52 \\ \hline
-    Farmington, NM & 1199.8 & 1.61 \\ \hline
-    Anchorage, AK & 1194.6 & 2.36 \\ \hline
-    Kansas City, MO-KS & 1159.4 & 3.16 \\ \hline
-    Memphis, TN-MS-AR & 1120.5 & 3.43 \\ \hline
-    Winston-Salem, NC & 1073.6 & 2.32 \\ \hline
-    Albuquerque, NM & 1043.4 & 4.53 \\ \hline
+    Farmington, NM & 1,199.8 & 1.61 \\ \hline
+    Anchorage, AK & 1,194.6 & 2.36 \\ \hline
+    Kansas City, MO-KS & 1,159.4 & 3.16 \\ \hline
+    Memphis, TN-MS-AR & 1,120.5 & 3.43 \\ \hline
+    Winston-Salem, NC & 1,073.6 & 2.32 \\ \hline
+    Albuquerque, NM & 1,043.4 & 4.53 \\ \hline
     Danville, IL & 935.7 & 0.00 \\ \hline
@@
 
-\par From the data collected by our Reddit scraper, we have seen that crime discussion is widespread among the selected communities.
+\par From the data collected by our Reddit crawler, we have seen that crime discussion is widespread among the selected communities.
 However, while we have analyzed posts about crime, we have not yet analyzed the users that initiate this crime discussion.
@@
 \par We have discussed the nature and prevalence of crime discussion on Reddit, a social media website, as it pertains to location-based communities.
-To obtain the necessary data and information, we have created a highly resilient Reddit scraper that fetches all posts from communities that represent the 384 Metropolitan Statistical Areas of the United States.
-The scraper gathered 161,166 posts over a two-month time span.
+To obtain the necessary data and information, we have created a highly resilient Reddit crawler that fetches all posts from communities that represent the 384 Metropolitan Statistical Areas of the United States.
+The crawler gathered 161,166 posts over a two-month time span.
 Of these 161,166 posts, a total of 6,792 were determined to discuss crime.
